---
title: "Supplement file: R code with Dta"
author: "Ellie Sherrard-Smith & Mercy Opiyo"
date: "11/01/2021"
output: pdf_document
---

## Analysis 0 Data

Data are available on request.

```{r setup, include = TRUE,  eval=FALSE}

###########################################################
##
## Questionnaire 1 Matutuine and Boane
## 
## 
library(dplyr)
library(plotly)
library(crosstalk)
library(htmltools)
library(DT)

setwd('C:/Users/esherrar/Documents/Mercy Opiyo/drive-download-20200520T105638Z-001')

setwd('data_questionnaire')

dec <- 1
df <- NULL
load('main_data_final_df.rdata')

df$calendarMonth <- format(as.Date(df$c_date), "%Y-%m")
m1df <- df[df$c_visit_month%in%'M1',] #houses in visit M1, assumed to be the total
q1c <- NULL
load('q1_choices_q1c.rdata')
load('common_data_final_wide_cdfw.rdata')#Data with of only common (c_) variables in wide format
q2 <- NULL#questionnaire 2
smrq2 <- NULL  #sleep modified room questionnaire 2
surq2 <- NULL  #sleep unmodified room questionnaire 2
load('q2.rdata')
load('smrq2.rdata')
load('surq2.rdata')



count_by_start_month_f = function(start_date, district){
  counter = numeric(6)
  Matut_houses_oct = sort(df$houseid[df$c_district == district & df$c_visit_month == "M1" & df$calendarMonth == start_date])
  counter[1] = length(Matut_houses_oct)
  m2_mat =sort(df$houseid[df$c_district == district & df$c_visit_month == "M2"])
  m2_mat_counta = match(Matut_houses_oct, m2_mat, nomatch = NA, incomparables = NULL)
  counter[2] = length(na.omit(m2_mat_counta))
  
  m3_mat =sort(df$houseid[df$c_district == district & df$c_visit_month == "M3"])
  m3_mat_counta = match(Matut_houses_oct, m3_mat, nomatch = NA, incomparables = NULL)
  counter[3] = length(na.omit(m3_mat_counta))
  
  m4_mat =sort(df$houseid[df$c_district == district & df$c_visit_month == "M4"])
  m4_mat_counta = match(Matut_houses_oct, m4_mat, nomatch = NA, incomparables = NULL)
  counter[4] = length(na.omit(m4_mat_counta))
  
  m5_mat =sort(df$houseid[df$c_district == district & df$c_visit_month == "M5"])
  m5_mat_counta = match(Matut_houses_oct, m5_mat, nomatch = NA, incomparables = NULL)
  counter[5] = length(na.omit(m5_mat_counta))
  
  m6_mat = sort(df$houseid[df$c_district == district & df$c_visit_month == "M6"])
  m6_mat_counta = match(Matut_houses_oct, m6_mat, nomatch = NA, incomparables = NULL)
  counter[6] = length(na.omit(m6_mat_counta))
  
  return(counter)
}
count_by_start_month_f(district = "Matutuine", start_date = sort(unique(df$calendarMonth))[1])
count_by_start_month_f(district = "Matutuine", start_date = sort(unique(df$calendarMonth))[2])
count_by_start_month_f(district = "Matutuine", start_date = sort(unique(df$calendarMonth))[3])

count_by_start_month_f(district = "Boane", start_date = sort(unique(df$calendarMonth))[1])
count_by_start_month_f(district = "Boane", start_date = sort(unique(df$calendarMonth))[2])
count_by_start_month_f(district = "Boane", start_date = sort(unique(df$calendarMonth))[3])
## This recreates the data in Table 1 main maunscript

## MATUTUINE
## This is our data for Houses tracked from October
Matut_houses_oct = subset(df,df$c_district == "Matutuine" & df$c_visit_month == "M1" & df$calendarMonth == sort(unique(df$calendarMonth))[1])

tapply(Matut_houses_oct$houseid,Matut_houses_oct$housesprayed,length)
for(i in 1:nrow(Matut_houses_oct)){
  Matut_houses_oct$total_rooms[i] = sum(Matut_houses_oct$c_combinedanimalroom[i],Matut_houses_oct$c_combinedlivingroom[i],
                                        Matut_houses_oct$c_combinedbedroom[i],Matut_houses_oct$c_combinedkitchen[i],
                                        Matut_houses_oct$c_combinedstorageroom[i],Matut_houses_oct$c_combinedbathroom[i],
                                        Matut_houses_oct$c_combinedgarage[i],Matut_houses_oct$c_combinedother[i],na.rm=TRUE)
  
  Matut_houses_oct$total_rooms_added[i] = sum(Matut_houses_oct$c_addedanimalroom[i],Matut_houses_oct$c_addedlivingroom[i],
                                        Matut_houses_oct$c_addedbedroom[i],Matut_houses_oct$c_addedkitchen[i],
                                        Matut_houses_oct$c_addedstorageroom[i],Matut_houses_oct$c_addedbathroom[i],
                                        Matut_houses_oct$c_addedgarage[i],Matut_houses_oct$c_addedother[i],na.rm=TRUE)
  
  Matut_houses_oct$total_rooms_mod[i] = sum(Matut_houses_oct$c_modifiedanimalroom[i],Matut_houses_oct$c_modifiedlivingroom[i],
                                        Matut_houses_oct$c_modifiedbedroom[i],Matut_houses_oct$c_modifiedkitchen[i],
                                        Matut_houses_oct$c_modifiedstorageroom[i],Matut_houses_oct$c_modifiedbathroom[i],
                                        Matut_houses_oct$c_modifiedgarage[i],Matut_houses_oct$c_modifiedother[i],na.rm=TRUE)
  
  
}
tapply(Matut_houses_oct$c_modifiedbedroom,Matut_houses_oct$c_combinedbedroom,length)
tapply(Matut_houses_oct$c_combinedbedroom,Matut_houses_oct$c_modifiedbedroom,length)
tapply(Matut_houses_oct$c_combinedbedroom,Matut_houses_oct$c_addedbedroom,length)
## 5 of the 43,  1 bedroom compounds
## 5 of the 31,  2 bedroom compounds
## 1 of the 19,  3 bedroom compounds
## 1 pf the 10,  4 bedroom compounds
## are modified
bedrooms = c(43,31,19,10,2,3,1,0,2,0,1) ## maximum 11 bedroons
modified_bedrooms = c(5,5,1,1,0,0,0,0,0,0,0)
added_bedrooms = rep(0,11)

tapply(Matut_houses_oct$c_modifiedlivingroom,Matut_houses_oct$c_combinedlivingroom,length)
tapply(Matut_houses_oct$c_combinedlivingroom,Matut_houses_oct$c_modifiedlivingroom,length)
tapply(Matut_houses_oct$c_combinedlivingroom,Matut_houses_oct$c_addedlivingroom,length)
## 11 0f the 68, 1 livingroom compounds
## 1 of the 20, 2 living room compounds
livingrooms = c(68,20,3,1,0,1,1)
modified_livingrooms = c(11,1,rep(0,5))
added_livingrooms = rep(0,7)

## no modifications in bathrooms
## no modifications in animal rooms
## no modifications in garages

tapply(Matut_houses_oct$c_modifiedkitchen,Matut_houses_oct$c_combinedkitchen,length)
tapply(Matut_houses_oct$c_combinedkitchen,Matut_houses_oct$c_modifiedkitchen,length)
tapply(Matut_houses_oct$c_combinedkitchen,Matut_houses_oct$c_addedkitchen,length)
## 2 0f the 33, 1 kitchen compounds
kitchens = c(33,3)
modified_kitchens = c(2,0)
added_kitchens = rep(0,2)

tapply(Matut_houses_oct$c_modifiedstorageroom,Matut_houses_oct$c_combinedstorageroom,length)
tapply(Matut_houses_oct$c_combinedstorageroom,Matut_houses_oct$c_modifiedstorageroom,length)
tapply(Matut_houses_oct$c_combinedstorageroom,Matut_houses_oct$c_addedstorageroom,length)
## 2 0f the 33, 1 kitchen compounds
storage = c(9,3,2,1,1)
modified_storage = c(0,1,0,0,0)
added_storage = rep(0,5)

to_plot_A = c(bedrooms,NA,livingrooms,NA,kitchens,NA,storage)
to_plot_B = c(modified_bedrooms,NA,modified_livingrooms,NA,modified_kitchens,NA,modified_storage)
cols_A = rep(adegenet::transp("grey",c(0.1,0.4,0.7,0.9)),c(12,8,3,5))

       
## Total compounds with any modified rooms in M1 october start
length(Matut_houses_oct$total_rooms_mod[Matut_houses_oct$total_rooms_mod > 0])



## Now for october start FOLLOW UP MONTHS
PULL_TOTAL_MOD_ADDED_FOR_Ms = function(dataInitHH,follow_up_month){
  ## Now for M2 october start
  m2_match =Matut_houses_oct$houseid
  Matut_houses_octM2temp2 = subset(df,df$c_district == "Matutuine" & df$c_visit_month == follow_up_month)
  Matut_houses_octM2 = Matut_houses_octM2temp2[Matut_houses_octM2temp2$houseid %in% m2_match, ]
  dim(Matut_houses_octM2)
  
  for(i in 1:nrow(Matut_houses_octM2)){
    Matut_houses_octM2$total_rooms[i] = sum(Matut_houses_octM2$c_combinedanimalroom[i],Matut_houses_octM2$c_combinedlivingroom[i],
                                            Matut_houses_octM2$c_combinedbedroom[i],Matut_houses_octM2$c_combinedkitchen[i],
                                            Matut_houses_octM2$c_combinedstorageroom[i],Matut_houses_octM2$c_combinedbathroom[i],
                                            Matut_houses_octM2$c_combinedgarage[i],Matut_houses_octM2$c_combinedother[i],na.rm=TRUE)
    
    Matut_houses_octM2$total_rooms_added[i] = sum(Matut_houses_octM2$c_addedanimalroom[i],Matut_houses_octM2$c_addedlivingroom[i],
                                                    Matut_houses_octM2$c_addedbedroom[i],Matut_houses_octM2$c_addedkitchen[i],
                                                    Matut_houses_octM2$c_addedstorageroom[i],Matut_houses_octM2$c_addedbathroom[i],
                                                    Matut_houses_octM2$c_addedgarage[i],Matut_houses_octM2$c_addedother[i],na.rm=TRUE)
    
    Matut_houses_octM2$total_rooms_mod[i] = sum(Matut_houses_octM2$c_modifiedanimalroom[i],Matut_houses_octM2$c_modifiedlivingroom[i],
                                                  Matut_houses_octM2$c_modifiedbedroom[i],Matut_houses_octM2$c_modifiedkitchen[i],
                                                  Matut_houses_octM2$c_modifiedstorageroom[i],Matut_houses_octM2$c_modifiedbathroom[i],
                                                  Matut_houses_octM2$c_modifiedgarage[i],Matut_houses_octM2$c_modifiedother[i],na.rm=TRUE)
    
    
  }
  return(
    list(
    c(length(Matut_houses_octM2$total_rooms_mod[Matut_houses_octM2$total_rooms_mod > 0]),
           length(Matut_houses_octM2$total_rooms_added[Matut_houses_octM2$total_rooms_added > 0])),
    Matut_houses_octM2
           )
  )
  
}
Matut_M2 = PULL_TOTAL_MOD_ADDED_FOR_Ms(dataInitHH = Matut_houses_oct$houseid,
                            follow_up_month = "M2")
Matut_M3 = PULL_TOTAL_MOD_ADDED_FOR_Ms(dataInitHH = Matut_houses_oct$houseid,
                            follow_up_month = "M3")
Matut_M4 = PULL_TOTAL_MOD_ADDED_FOR_Ms(dataInitHH = Matut_houses_oct$houseid,
                            follow_up_month = "M4")
Matut_M5 = PULL_TOTAL_MOD_ADDED_FOR_Ms(dataInitHH = Matut_houses_oct$houseid,
                            follow_up_month = "M5")
Matut_M6 = PULL_TOTAL_MOD_ADDED_FOR_Ms(dataInitHH = Matut_houses_oct$houseid,
                            follow_up_month = "M6")

## For Table 1: modified rooms
c(length(Matut_houses_oct$total_rooms_mod[Matut_houses_oct$total_rooms_mod > 0]),
  Matut_M2[[1]][1],Matut_M3[[1]][1],Matut_M4[[1]][1],Matut_M5[[1]][1],Matut_M6[[1]][1])

c(length(Matut_houses_oct$total_rooms_added[Matut_houses_oct$total_rooms_added > 0]),
  Matut_M2[[1]][2],Matut_M3[[1]][2],Matut_M4[[1]][2],Matut_M5[[1]][2],Matut_M6[[1]][2])

sum(Matut_M2[[2]]$total_rooms_added)
sum(Matut_M2[[2]]$total_rooms_mod)


tapply(Matut_M6[[2]]$c_combinedbedroom,Matut_M6[[2]]$c_modifiedbedroom,length)
modified_bedrooms_M6 = c(4,4,1,0,0,0,0,0,0,0,0)##11
tapply(Matut_M6[[2]]$c_combinedlivingroom,Matut_M6[[2]]$c_modifiedlivingroom,length)
tapply(Matut_M6[[2]]$c_combinedkitchen,Matut_M6[[2]]$c_modifiedkitchen,length)
tapply(Matut_M6[[2]]$c_combinedstorageroom,Matut_M6[[2]]$c_modifiedstorageroom,length)
modified_livingrooms_M6 = c(12,0,0,0,0,0,0)##7
modified_kitchens_M6 = c(1,0)##2
modified_storage_M6 = c(1,0,0,0,0)##5

tapply(Matut_M5[[2]]$c_combinedbedroom,Matut_M5[[2]]$c_modifiedbedroom,length)
modified_bedrooms_M5 = c(6,3,0,0,0,0,0,0,0,0,0)##11
tapply(Matut_M5[[2]]$c_combinedlivingroom,Matut_M5[[2]]$c_modifiedlivingroom,length)
tapply(Matut_M5[[2]]$c_combinedkitchen,Matut_M5[[2]]$c_modifiedkitchen,length)
tapply(Matut_M5[[2]]$c_combinedstorageroom,Matut_M5[[2]]$c_modifiedstorageroom,length)
modified_livingrooms_M5 = c(12,0,0,0,0,0,0)##7
modified_kitchens_M5 = c(0,0)##2
modified_storage_M5 = c(1,0,0,0,0)##5

tapply(Matut_M4[[2]]$c_combinedbedroom,Matut_M4[[2]]$c_modifiedbedroom,length)
modified_bedrooms_M4 = c(14,3,0,0,0,0,0,0,0,0,0)##11
tapply(Matut_M4[[2]]$c_combinedlivingroom,Matut_M4[[2]]$c_modifiedlivingroom,length)
tapply(Matut_M4[[2]]$c_combinedkitchen,Matut_M4[[2]]$c_modifiedkitchen,length)
tapply(Matut_M4[[2]]$c_combinedstorageroom,Matut_M4[[2]]$c_modifiedstorageroom,length)
modified_livingrooms_M4 = c(15,0,0,0,0,0,0)##7
modified_kitchens_M4 = c(1,0)##2
modified_storage_M4 = c(1,0,0,0,0)##5


tapply(Matut_M3[[2]]$c_combinedbedroom,Matut_M3[[2]]$c_modifiedbedroom,length)
modified_bedrooms_M3 = c(12,5,0,0,0,0,0,0,0,0,0)##11
tapply(Matut_M3[[2]]$c_combinedlivingroom,Matut_M3[[2]]$c_modifiedlivingroom,length)
tapply(Matut_M3[[2]]$c_combinedkitchen,Matut_M3[[2]]$c_modifiedkitchen,length)
tapply(Matut_M3[[2]]$c_combinedstorageroom,Matut_M3[[2]]$c_modifiedstorageroom,length)
modified_livingrooms_M3 = c(11,0,0,0,0,0,0)##7
modified_kitchens_M3 = c(0,0)##2
modified_storage_M3 = c(1,0,0,0,0)##5


tapply(Matut_M2[[2]]$c_combinedbedroom,Matut_M2[[2]]$c_modifiedbedroom,length)
modified_bedrooms_M2 = c(3,1,0,0,0,0,0,0,0,0,0)##11
tapply(Matut_M2[[2]]$c_combinedlivingroom,Matut_M2[[2]]$c_modifiedlivingroom,length)
tapply(Matut_M2[[2]]$c_combinedkitchen,Matut_M2[[2]]$c_modifiedkitchen,length)
tapply(Matut_M2[[2]]$c_combinedstorageroom,Matut_M2[[2]]$c_modifiedstorageroom,length)
modified_livingrooms_M2 = c(6,0,0,0,0,0,0)##7
modified_kitchens_M2 = c(0,0)##2
modified_storage_M2 = c(0,0,0,0,0)##5


96/sum(Matut_houses_oct$c_combinedbedroom,na.rm = T)
69/sum(Matut_houses_oct$c_combinedlivingroom,na.rm = T)

to_plot_A = c(bedrooms,NA,livingrooms,NA,kitchens,NA,storage)
to_plot_M6 = c(modified_bedrooms+modified_bedrooms_M2+modified_bedrooms_M3+modified_bedrooms_M4+modified_bedrooms_M5+modified_bedrooms_M6,NA,modified_livingrooms+modified_livingrooms_M2+modified_livingrooms_M3+modified_livingrooms_M4+modified_livingrooms_M5+modified_livingrooms_M6,NA,modified_kitchens+modified_kitchens_M4+modified_kitchens_M6,NA,modified_storage+modified_storage_M3+modified_storage_M4+modified_storage_M5++modified_storage_M6)
to_plot_M5 = c(modified_bedrooms+modified_bedrooms_M2+modified_bedrooms_M3+modified_bedrooms_M4+modified_bedrooms_M5,                     NA,modified_livingrooms+modified_livingrooms_M2+modified_livingrooms_M3+modified_livingrooms_M4+modified_livingrooms_M5,                        NA,modified_kitchens+modified_kitchens_M4,                     NA,modified_storage+modified_storage_M3+modified_storage_M4+modified_storage_M5)##GREEN
to_plot_M4 = c(modified_bedrooms+modified_bedrooms_M2+modified_bedrooms_M3+modified_bedrooms_M4,                                          NA,modified_livingrooms+modified_livingrooms_M2+modified_livingrooms_M3+modified_livingrooms_M4,                                                NA,modified_kitchens+modified_kitchens_M4,                     NA,modified_storage+modified_storage_M3+modified_storage_M4)##RED
to_plot_M3 = c(modified_bedrooms+modified_bedrooms_M2+modified_bedrooms_M3,                                                               NA,modified_livingrooms+modified_livingrooms_M2+modified_livingrooms_M3,                                                                        NA,modified_kitchens,                                          NA,modified_storage+modified_storage_M3)##BLUE
to_plot_M2 = c(modified_bedrooms+modified_bedrooms_M2,                                                                                    NA,modified_livingrooms+modified_livingrooms_M2,                                                                                                NA,modified_kitchens,                                          NA,modified_storage)##PURPLE
to_plot_M1 = c(modified_bedrooms,NA,modified_livingrooms,NA,modified_kitchens,NA,modified_storage)##ORANGE

length(to_plot_A);length(to_plot_M6);length(to_plot_M5);length(to_plot_M4);length(to_plot_M3);length(to_plot_M2);length(to_plot_M1)

sum(to_plot_M6,na.rm=TRUE)
##TOTAL ROOMS MODIFIED
FROM_to_plot_M6 = c(c(modified_bedrooms+modified_bedrooms_M2+modified_bedrooms_M3+modified_bedrooms_M4+modified_bedrooms_M5+modified_bedrooms_M6)*c(1:11),
                    c(modified_livingrooms+modified_livingrooms_M2+modified_livingrooms_M3+modified_livingrooms_M4+modified_livingrooms_M5+modified_livingrooms_M6)*c(1:7),
                    c(modified_kitchens+modified_kitchens_M2+modified_kitchens_M3+modified_kitchens_M4+modified_kitchens_M5+modified_kitchens_M6)*c(1:2),
                    c(modified_storage+modified_storage_M2+modified_storage_M3+modified_storage_M4+modified_storage_M5+modified_storage_M6)*c(1:5))
sum(FROM_to_plot_M6,na.rm=TRUE)


cols_A = rep(adegenet::transp("grey",c(0.1,0.4,0.7,0.9)),c(12,8,3,5))



### And added rooms?

tapply(Matut_M6[[2]]$c_combinedbedroom,Matut_M6[[2]]$c_addedbedroom,length)
added_bedrooms_M6 = c(6,1,0,0,0,0,0,0,0,0,0)##11
tapply(Matut_M6[[2]]$c_combinedlivingroom,Matut_M6[[2]]$c_addedlivingroom,length)
tapply(Matut_M6[[2]]$c_combinedkitchen,Matut_M6[[2]]$c_addedkitchen,length)
tapply(Matut_M6[[2]]$c_combinedstorageroom,Matut_M6[[2]]$c_addedstorageroom,length)
added_livingrooms_M6 = c(4,0,0,0,0,0,0)##7
added_kitchens_M6 = c(0,0)##2
added_storage_M6 = c(1,0,0,0,0)##5

tapply(Matut_M5[[2]]$c_combinedbedroom,Matut_M5[[2]]$c_addedbedroom,length)
added_bedrooms_M5 = c(5,3,0,0,0,0,0,0,0,0,0)##11
tapply(Matut_M5[[2]]$c_combinedlivingroom,Matut_M5[[2]]$c_addedlivingroom,length)
tapply(Matut_M5[[2]]$c_combinedkitchen,Matut_M5[[2]]$c_addedkitchen,length)
tapply(Matut_M5[[2]]$c_combinedstorageroom,Matut_M5[[2]]$c_addedstorageroom,length)
added_livingrooms_M5 = c(3,0,0,0,0,0,0)##7
added_kitchens_M5 = c(0,0)##2
added_storage_M5 = c(2,0,0,0,0)##5

tapply(Matut_M4[[2]]$c_combinedbedroom,Matut_M4[[2]]$c_addedbedroom,length)
added_bedrooms_M4 = c(6,3,0,0,0,0,0,0,0,0,0)##11
tapply(Matut_M4[[2]]$c_combinedlivingroom,Matut_M4[[2]]$c_addedlivingroom,length)
tapply(Matut_M4[[2]]$c_combinedkitchen,Matut_M4[[2]]$c_addedkitchen,length)
tapply(Matut_M4[[2]]$c_combinedstorageroom,Matut_M4[[2]]$c_addedstorageroom,length)
added_livingrooms_M4 = c(2,0,0,0,0,0,0)##7
added_kitchens_M4 = c(2,0)##2
added_storage_M4 = c(1,0,0,0,0)##5


tapply(Matut_M3[[2]]$c_combinedbedroom,Matut_M3[[2]]$c_addedbedroom,length)
added_bedrooms_M3 = c(12,5,0,0,0,0,0,0,0,0,0)##11
tapply(Matut_M3[[2]]$c_combinedlivingroom,Matut_M3[[2]]$c_addedlivingroom,length)
tapply(Matut_M3[[2]]$c_combinedkitchen,Matut_M3[[2]]$c_addedkitchen,length)
tapply(Matut_M3[[2]]$c_combinedstorageroom,Matut_M3[[2]]$c_addedstorageroom,length)
added_livingrooms_M3 = c(11,0,0,0,0,0,0)##7
added_kitchens_M3 = c(0,0)##2
added_storage_M3 = c(1,0,0,0,0)##5


tapply(Matut_M2[[2]]$c_combinedbedroom,Matut_M2[[2]]$c_addedbedroom,length)
added_bedrooms_M2 = c(5,1,0,0,0,0,0,0,0,0,0)##11
tapply(Matut_M2[[2]]$c_combinedlivingroom,Matut_M2[[2]]$c_addedlivingroom,length)
tapply(Matut_M2[[2]]$c_combinedkitchen,Matut_M2[[2]]$c_addedkitchen,length)
tapply(Matut_M2[[2]]$c_combinedkitchen,Matut_M2[[2]]$c_addedstorageroom,length)
added_livingrooms_M2 = c(1,1,0,0,0,0,0)##7
added_kitchens_M2 = c(4,0)##2
added_storage_M2 = c(2,0,0,0,0)##5

## (There were no added rooms in M1)


### Figure 3 in the main manuscript

par(mfrow=c(2,1))

to_plota_M6 = c(added_bedrooms_M2+added_bedrooms_M3+added_bedrooms_M4+added_bedrooms_M5+added_bedrooms_M6,NA,added_livingrooms_M2+added_livingrooms_M3+added_livingrooms_M4+added_livingrooms_M5+added_livingrooms_M6, NA,added_kitchens_M2+added_kitchens_M3+added_kitchens_M4+added_kitchens_M5+added_kitchens_M6,NA,added_storage_M2+added_storage_M3+added_storage_M4+added_storage_M5++added_storage_M6)
to_plota_M5 = c(added_bedrooms_M2+added_bedrooms_M3+added_bedrooms_M4+added_bedrooms_M5,                  NA,added_livingrooms_M2+added_livingrooms_M3+added_livingrooms_M4+added_livingrooms_M5,                      NA,added_kitchens_M2+added_kitchens_M3+added_kitchens_M4+added_kitchens_M5,                  NA,added_storage_M2+added_storage_M3+added_storage_M4+added_storage_M5)##GREEN
to_plota_M4 = c(added_bedrooms_M2+added_bedrooms_M3+added_bedrooms_M4,                                    NA,added_livingrooms_M2+added_livingrooms_M3+added_livingrooms_M4,                                           NA,added_kitchens_M2+added_kitchens_M3+added_kitchens_M4,                                    NA,added_storage_M2+added_storage_M3+added_storage_M4)##RED
to_plota_M3 = c(added_bedrooms_M2+added_bedrooms_M3,                                                      NA,added_livingrooms_M2+added_livingrooms_M3,                                                                NA,added_kitchens_M2+added_kitchens_M3,                                                      NA,added_storage_M2+added_storage_M3)##BLUE
to_plota_M2 = c(added_bedrooms_M2,                                                                        NA,added_livingrooms_M2,                                                                                     NA,added_kitchens_M2,                                                                        NA,added_storage_M2)##PURPLE




cols_A = rep(adegenet::transp("grey",c(0.1,0.4,0.7,0.9)),c(12,8,3,5))

barplot(to_plot_A+to_plota_M6,col=cols_A,lty=2,
        xlab="Rooms in compounds",xaxt="n",yaxt="n",
        ylab="Frequency", main = "Matutuine (October cohort)")
barplot(to_plot_A+to_plota_M5,add=TRUE,col = adegenet::transp("grey",0.2),
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
barplot(to_plot_A+to_plota_M4,add=TRUE,col = adegenet::transp("grey",0.2),
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
barplot(to_plot_A+to_plota_M3,add=TRUE,col = adegenet::transp("grey",0.2),
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
barplot(to_plot_A+to_plota_M2,add=TRUE,col = adegenet::transp("grey",0.2),
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
barplot(to_plot_A,add=TRUE,col = adegenet::transp("grey",0.2),
        xlab="",xaxt="n",yaxt="n",
        ylab="", main = "")


barplot(to_plot_M6,add=TRUE,col = adegenet::transp("yellow",0.7),
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
barplot(to_plot_M5,add=TRUE,col = adegenet::transp("orange",0.3),
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
barplot(to_plot_M4,add=TRUE,col = adegenet::transp("orange",0.3),
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
barplot(to_plot_M3,add=TRUE,col = adegenet::transp("orange"),
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
barplot(to_plot_M2,add=TRUE,col = adegenet::transp("darkred",0.7),
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
barplot(to_plot_M1,add=TRUE,col = "darkred",
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
axis(1,at=seq(1,33,length=28),
     labels=c(1:11,NA,1:7,NA,1:2,NA,1:5))
axis(2,las=2, at=c(0,10,20,30,40,50,60,70,80,90))

abline(v=14,lty=2,lwd=2,col="grey20")
text(7,50,"Bedrooms")

abline(v=23.5,lty=2,lwd=2,col="grey20")
text(18.7,50,"Living rooms")

abline(v=27,lty=2,lwd=2,col="grey20")
text(25,50,"Kitchens")
text(30,50,"Storage rooms")

legend(2.6,90,
       legend = c("Added rooms (above solid line)",
                  "Modified rooms","M1 - M6 (Darker to paler shades)"),
       col=c("grey70","orange",NA),pch=15,bty="n",cex=1)



##
## REPEAT FOR BOANE
## This is our data for Houses tracked from October
Boane_houses_oct = subset(df,df$c_district == "Boane" & df$c_visit_month == "M1" & df$calendarMonth == sort(unique(df$calendarMonth))[1])

tapply(Boane_houses_oct$houseid,Boane_houses_oct$housesprayed,length)
for(i in 1:nrow(Boane_houses_oct)){
  Boane_houses_oct$total_rooms[i] = sum(Boane_houses_oct$c_combinedanimalroom[i],Boane_houses_oct$c_combinedlivingroom[i],
                                        Boane_houses_oct$c_combinedbedroom[i],Boane_houses_oct$c_combinedkitchen[i],
                                        Boane_houses_oct$c_combinedstorageroom[i],Boane_houses_oct$c_combinedbathroom[i],
                                        Boane_houses_oct$c_combinedgarage[i],Boane_houses_oct$c_combinedother[i],na.rm=TRUE)
  
  Boane_houses_oct$total_rooms_added[i] = sum(Boane_houses_oct$c_addedanimalroom[i],Boane_houses_oct$c_addedlivingroom[i],
                                              Boane_houses_oct$c_addedbedroom[i],Boane_houses_oct$c_addedkitchen[i],
                                              Boane_houses_oct$c_addedstorageroom[i],Boane_houses_oct$c_addedbathroom[i],
                                              Boane_houses_oct$c_addedgarage[i],Boane_houses_oct$c_addedother[i],na.rm=TRUE)
  
  Boane_houses_oct$total_rooms_mod[i] = sum(Boane_houses_oct$c_modifiedanimalroom[i],Boane_houses_oct$c_modifiedlivingroom[i],
                                            Boane_houses_oct$c_modifiedbedroom[i],Boane_houses_oct$c_modifiedkitchen[i],
                                            Boane_houses_oct$c_modifiedstorageroom[i],Boane_houses_oct$c_modifiedbathroom[i],
                                            Boane_houses_oct$c_modifiedgarage[i],Boane_houses_oct$c_modifiedother[i],na.rm=TRUE)
  
  
}
tapply(Boane_houses_oct$c_modifiedbedroom,Boane_houses_oct$c_combinedbedroom,length)
tapply(Boane_houses_oct$c_combinedbedroom,Boane_houses_oct$c_modifiedbedroom,length)
tapply(Boane_houses_oct$c_combinedbedroom,Boane_houses_oct$c_addedbedroom,length)
## are modified
bedrooms = c(19,35,25,3,4) ## maximum 5 bedroons
modified_bedrooms = c(1,0,1,0,0)

tapply(Boane_houses_oct$c_modifiedlivingroom,Boane_houses_oct$c_combinedlivingroom,length)
tapply(Boane_houses_oct$c_combinedlivingroom,Boane_houses_oct$c_modifiedlivingroom,length)
tapply(Boane_houses_oct$c_combinedlivingroom,Boane_houses_oct$c_addedlivingroom,length)
## living room compounds
livingrooms = c(65,11)
modified_livingrooms = c(3,1)

## no modifications in bathrooms
## no modifications in animal rooms
## no modifications in garages

tapply(Boane_houses_oct$c_modifiedkitchen,Boane_houses_oct$c_combinedkitchen,length)
tapply(Boane_houses_oct$c_combinedkitchen,Boane_houses_oct$c_modifiedkitchen,length)
tapply(Boane_houses_oct$c_combinedkitchen,Boane_houses_oct$c_addedkitchen,length)
## 2 0f the 33, 1 kitchen compounds
kitchens = c(21)
modified_kitchens = c(0)

tapply(Boane_houses_oct$c_modifiedstorageroom,Boane_houses_oct$c_combinedstorageroom,length)
tapply(Boane_houses_oct$c_combinedstorageroom,Boane_houses_oct$c_modifiedstorageroom,length)
tapply(Boane_houses_oct$c_combinedstorageroom,Boane_houses_oct$c_addedstorageroom,length)
## 2 0f the 33, 1 kitchen compounds
storage = c(4)
modified_storage = c(0)

to_plot_A = c(bedrooms,NA,livingrooms,NA,kitchens,NA,storage)
# to_plot_B = c(modified_bedrooms,NA,modified_livingrooms,NA,0,NA,0)
cols_A = rep(adegenet::transp("grey",c(0.1,0.4,0.7,0.9)),c(6,3,2,2))


## Total compounds with any modified rooms in M1 october start
length(Boane_houses_oct$total_rooms_mod[Boane_houses_oct$total_rooms_mod > 0])



## Now for october start FOLLOW UP MONTHS
PULL_TOTAL_MOD_ADDED_FOR_Ms = function(dataInitHH,follow_up_month){
  ## Now for M2 october start
  m2_match = Boane_houses_oct$houseid
  Boane_houses_octM2temp2 = subset(df,df$c_district == "Boane" & df$c_visit_month == follow_up_month)
  Boane_houses_octM2 = Boane_houses_octM2temp2[Boane_houses_octM2temp2$houseid %in% m2_match, ]
  dim(Boane_houses_octM2)
  
  for(i in 1:nrow(Boane_houses_octM2)){
    Boane_houses_octM2$total_rooms[i] = sum(Boane_houses_octM2$c_combinedanimalroom[i],Boane_houses_octM2$c_combinedlivingroom[i],
                                            Boane_houses_octM2$c_combinedbedroom[i],Boane_houses_octM2$c_combinedkitchen[i],
                                            Boane_houses_octM2$c_combinedstorageroom[i],Boane_houses_octM2$c_combinedbathroom[i],
                                            Boane_houses_octM2$c_combinedgarage[i],Boane_houses_octM2$c_combinedother[i],na.rm=TRUE)
    
    Boane_houses_octM2$total_rooms_added[i] = sum(Boane_houses_octM2$c_addedanimalroom[i],Boane_houses_octM2$c_addedlivingroom[i],
                                                  Boane_houses_octM2$c_addedbedroom[i],Boane_houses_octM2$c_addedkitchen[i],
                                                  Boane_houses_octM2$c_addedstorageroom[i],Boane_houses_octM2$c_addedbathroom[i],
                                                  Boane_houses_octM2$c_addedgarage[i],Boane_houses_octM2$c_addedother[i],na.rm=TRUE)
    
    Boane_houses_octM2$total_rooms_mod[i] = sum(Boane_houses_octM2$c_modifiedanimalroom[i],Boane_houses_octM2$c_modifiedlivingroom[i],
                                                Boane_houses_octM2$c_modifiedbedroom[i],Boane_houses_octM2$c_modifiedkitchen[i],
                                                Boane_houses_octM2$c_modifiedstorageroom[i],Boane_houses_octM2$c_modifiedbathroom[i],
                                                Boane_houses_octM2$c_modifiedgarage[i],Boane_houses_octM2$c_modifiedother[i],na.rm=TRUE)
    
    
  }
  return(
    list(
      c(length(Boane_houses_octM2$total_rooms_mod[Boane_houses_octM2$total_rooms_mod > 0]),
        length(Boane_houses_octM2$total_rooms_added[Boane_houses_octM2$total_rooms_added > 0])),
      Boane_houses_octM2
    )
  )
  
}
Boane_M2 = PULL_TOTAL_MOD_ADDED_FOR_Ms(dataInitHH = Boane_houses_oct$houseid,
                                       follow_up_month = "M2")
Boane_M3 = PULL_TOTAL_MOD_ADDED_FOR_Ms(dataInitHH = Boane_houses_oct$houseid,
                                       follow_up_month = "M3")
Boane_M4 = PULL_TOTAL_MOD_ADDED_FOR_Ms(dataInitHH = Boane_houses_oct$houseid,
                                       follow_up_month = "M4")
Boane_M5 = PULL_TOTAL_MOD_ADDED_FOR_Ms(dataInitHH = Boane_houses_oct$houseid,
                                       follow_up_month = "M5")
Boane_M6 = PULL_TOTAL_MOD_ADDED_FOR_Ms(dataInitHH = Boane_houses_oct$houseid,
                                       follow_up_month = "M6")

## For Table 1: modified rooms
c(length(Boane_houses_oct$total_rooms_mod[Boane_houses_oct$total_rooms_mod > 0]),
  Boane_M2[[1]][1],Boane_M3[[1]][1],Boane_M4[[1]][1],Boane_M5[[1]][1],Boane_M6[[1]][1])

c(length(Boane_houses_oct$total_rooms_added[Boane_houses_oct$total_rooms_added > 0]),
  Boane_M2[[1]][2],Boane_M3[[1]][2],Boane_M4[[1]][2],Boane_M5[[1]][2],Boane_M6[[1]][2])


tapply(Boane_M6[[2]]$c_combinedbedroom,Boane_M6[[2]]$c_modifiedbedroom,length)
modified_bedrooms_M6 = c(0,0,0,0,0)##5
tapply(Boane_M6[[2]]$c_combinedlivingroom,Boane_M6[[2]]$c_modifiedlivingroom,length)
tapply(Boane_M6[[2]]$c_combinedkitchen,Boane_M6[[2]]$c_modifiedkitchen,length)
tapply(Boane_M6[[2]]$c_combinedstorageroom,Boane_M6[[2]]$c_modifiedstorageroom,length)
modified_livingrooms_M6 = c(0,0)##2
modified_kitchens_M6 = c(0)##1
modified_storage_M6 = c(0)##1

tapply(Boane_M5[[2]]$c_combinedbedroom,Boane_M5[[2]]$c_modifiedbedroom,length)
modified_bedrooms_M5 = c(0,0,0,0,0)##11
tapply(Boane_M5[[2]]$c_combinedlivingroom,Boane_M5[[2]]$c_modifiedlivingroom,length)
tapply(Boane_M5[[2]]$c_combinedkitchen,Boane_M5[[2]]$c_modifiedkitchen,length)
tapply(Boane_M5[[2]]$c_combinedstorageroom,Boane_M5[[2]]$c_modifiedstorageroom,length)
modified_livingrooms_M5 = c(0,0)##2
modified_kitchens_M5 = c(0)##1
modified_storage_M5 = c(0)##1


tapply(Boane_M4[[2]]$c_combinedbedroom,Boane_M4[[2]]$c_modifiedbedroom,length)
modified_bedrooms_M4 = c(0,0,0,0,0)##11
tapply(Boane_M4[[2]]$c_combinedlivingroom,Boane_M4[[2]]$c_modifiedlivingroom,length)
tapply(Boane_M4[[2]]$c_combinedkitchen,Boane_M4[[2]]$c_modifiedkitchen,length)
tapply(Boane_M4[[2]]$c_combinedstorageroom,Boane_M4[[2]]$c_modifiedstorageroom,length)
modified_livingrooms_M4 = c(0,0)##7
modified_kitchens_M4 = c(0)##2
modified_storage_M4 = c(0)##5


tapply(Boane_M3[[2]]$c_combinedbedroom,Boane_M3[[2]]$c_modifiedbedroom,length)
modified_bedrooms_M3 = c(0,1,1,0,0)##11
tapply(Boane_M3[[2]]$c_combinedlivingroom,Boane_M3[[2]]$c_modifiedlivingroom,length)
tapply(Boane_M3[[2]]$c_combinedkitchen,Boane_M3[[2]]$c_modifiedkitchen,length)
tapply(Boane_M3[[2]]$c_combinedstorageroom,Boane_M3[[2]]$c_modifiedstorageroom,length)
modified_livingrooms_M3 = c(1,0)##7
modified_kitchens_M3 = c(0)##2
modified_storage_M3 = c(0)##5


tapply(Boane_M2[[2]]$c_combinedbedroom,Boane_M2[[2]]$c_modifiedbedroom,length)
modified_bedrooms_M2 = c(0,0,0,0,0)##11
tapply(Boane_M2[[2]]$c_combinedlivingroom,Boane_M2[[2]]$c_modifiedlivingroom,length)
tapply(Boane_M2[[2]]$c_combinedkitchen,Boane_M2[[2]]$c_modifiedkitchen,length)
tapply(Boane_M2[[2]]$c_combinedstorageroom,Boane_M2[[2]]$c_modifiedstorageroom,length)
modified_livingrooms_M2 = c(0,0)##7
modified_kitchens_M2 = c(0)##2
modified_storage_M2 = c(0)##5

9/sum(Boane_houses_oct$c_combinedbedroom,na.rm = T)
6/sum(Boane_houses_oct$c_combinedlivingroom,na.rm = T)

to_plot_A = c(bedrooms,NA,livingrooms,NA,kitchens,NA,storage)
to_plot_M6 = c(modified_bedrooms+modified_bedrooms_M2+modified_bedrooms_M3+modified_bedrooms_M4+modified_bedrooms_M5+modified_bedrooms_M6,NA,modified_livingrooms+modified_livingrooms_M2+modified_livingrooms_M3+modified_livingrooms_M4+modified_livingrooms_M5+modified_livingrooms_M6,NA,modified_kitchens+modified_kitchens_M2+modified_kitchens_M3+modified_kitchens_M4+modified_kitchens_M5+modified_kitchens_M6,NA,0)
to_plot_M5 = c(modified_bedrooms+modified_bedrooms_M2+modified_bedrooms_M3+modified_bedrooms_M4+modified_bedrooms_M5,                     NA,modified_livingrooms+modified_livingrooms_M2+modified_livingrooms_M3+modified_livingrooms_M4+modified_livingrooms_M5,                        NA,modified_kitchens+modified_kitchens_M2+modified_kitchens_M3+modified_kitchens_M4+modified_kitchens_M5,                     NA,0)##GREEN
to_plot_M4 = c(modified_bedrooms+modified_bedrooms_M2+modified_bedrooms_M3+modified_bedrooms_M4,                                          NA,modified_livingrooms+modified_livingrooms_M2+modified_livingrooms_M3+modified_livingrooms_M4,                                                NA,modified_kitchens+modified_kitchens_M2+modified_kitchens_M3+modified_kitchens_M4,                                          NA,0)##RED
to_plot_M3 = c(modified_bedrooms+modified_bedrooms_M2+modified_bedrooms_M3,                                                               NA,modified_livingrooms+modified_livingrooms_M2+modified_livingrooms_M3,                                                                        NA,modified_kitchens+modified_kitchens_M2+modified_kitchens_M3,                                                               NA,0)##BLUE
to_plot_M2 = c(modified_bedrooms+modified_bedrooms_M2,                                                                                    NA,modified_livingrooms+modified_livingrooms_M2,                                                                                                NA,modified_kitchens+modified_kitchens_M2,                                                                                    NA,0)##PURPLE
to_plot_M1 = c(modified_bedrooms,NA,modified_livingrooms,NA,modified_kitchens,NA,modified_storage)##ORANGE

length(to_plot_A);length(to_plot_M6);length(to_plot_M5);length(to_plot_M4);length(to_plot_M3);length(to_plot_M2);length(to_plot_M1)

cols_A = rep(adegenet::transp("grey",c(0.1,0.4,0.7,0.9)),c(6,3,2,2))

### And added rooms?

tapply(Boane_M6[[2]]$c_combinedbedroom,Boane_M6[[2]]$c_addedbedroom,length)
added_bedrooms_M6 = c(0,0,0,0,0)##5
tapply(Boane_M6[[2]]$c_combinedlivingroom,Boane_M6[[2]]$c_addedlivingroom,length)
tapply(Boane_M6[[2]]$c_combinedkitchen,Boane_M6[[2]]$c_addedkitchen,length)
tapply(Boane_M6[[2]]$c_combinedstorageroom,Boane_M6[[2]]$c_addedstorageroom,length)
added_livingrooms_M6 = c(0,0)##2
added_kitchens_M6 = c(1)##1
added_storage_M6 = c(0)##1

tapply(Boane_M5[[2]]$c_combinedbedroom,Boane_M5[[2]]$c_addedbedroom,length)
added_bedrooms_M5 = c(0,0,0,0,0)##11
tapply(Boane_M5[[2]]$c_combinedlivingroom,Boane_M5[[2]]$c_addedlivingroom,length)
tapply(Boane_M5[[2]]$c_combinedkitchen,Boane_M5[[2]]$c_addedkitchen,length)
tapply(Boane_M5[[2]]$c_combinedstorageroom,Boane_M5[[2]]$c_addedstorageroom,length)
added_livingrooms_M5 = c(0,0)##2
added_kitchens_M5 = c(0)##1
added_storage_M5 = c(0)##1

tapply(Boane_M4[[2]]$c_combinedbedroom,Boane_M4[[2]]$c_addedbedroom,length)
added_bedrooms_M4 = c(1,0,0,0,0)##11
tapply(Boane_M4[[2]]$c_combinedlivingroom,Boane_M4[[2]]$c_addedlivingroom,length)
tapply(Boane_M4[[2]]$c_combinedkitchen,Boane_M4[[2]]$c_addedkitchen,length)
tapply(Boane_M4[[2]]$c_combinedstorageroom,Boane_M4[[2]]$c_addedstorageroom,length)
added_livingrooms_M4 = c(0,0)##7
added_kitchens_M4 = c(0)##2
added_storage_M4 = c(0)##5


tapply(Boane_M3[[2]]$c_combinedbedroom,Boane_M3[[2]]$c_addedbedroom,length)
added_bedrooms_M3 = c(1,0,0,0,0)##11
tapply(Boane_M3[[2]]$c_combinedlivingroom,Boane_M3[[2]]$c_addedlivingroom,length)
tapply(Boane_M3[[2]]$c_combinedkitchen,Boane_M3[[2]]$c_addedkitchen,length)
tapply(Boane_M3[[2]]$c_combinedstorageroom,Boane_M3[[2]]$c_addedstorageroom,length)
added_livingrooms_M3 = c(0,0)##7
added_kitchens_M3 = c(0)##2
added_storage_M3 = c(0)##5


tapply(Boane_M2[[2]]$c_combinedbedroom,Boane_M2[[2]]$c_addedbedroom,length)
added_bedrooms_M2 = c(0,0,0,0,0)##11
tapply(Boane_M2[[2]]$c_combinedlivingroom,Boane_M2[[2]]$c_addedlivingroom,length)
tapply(Boane_M2[[2]]$c_combinedkitchen,Boane_M2[[2]]$c_addedkitchen,length)
tapply(Boane_M2[[2]]$c_combinedkitchen,Boane_M2[[2]]$c_addedstorageroom,length)
added_livingrooms_M2 = c(0,0)##7
added_kitchens_M2 = c(0)##2
added_storage_M2 = c(0)##5

## (There were no added rooms in M1)

# par(mfrow=c(2,1))

to_plota_M6 = c(added_bedrooms_M2+added_bedrooms_M3+added_bedrooms_M4+added_bedrooms_M5+added_bedrooms_M6,NA,added_livingrooms_M2+added_livingrooms_M3+added_livingrooms_M4+added_livingrooms_M5+added_livingrooms_M6, NA,added_kitchens_M2+added_kitchens_M3+added_kitchens_M4+added_kitchens_M5+added_kitchens_M6,NA,added_storage_M2+added_storage_M3+added_storage_M4+added_storage_M5++added_storage_M6)
to_plota_M5 = c(added_bedrooms_M2+added_bedrooms_M3+added_bedrooms_M4+added_bedrooms_M5,                  NA,added_livingrooms_M2+added_livingrooms_M3+added_livingrooms_M4+added_livingrooms_M5,                      NA,added_kitchens_M2+added_kitchens_M3+added_kitchens_M4+added_kitchens_M5,                  NA,added_storage_M2+added_storage_M3+added_storage_M4+added_storage_M5)##GREEN
to_plota_M4 = c(added_bedrooms_M2+added_bedrooms_M3+added_bedrooms_M4,                                    NA,added_livingrooms_M2+added_livingrooms_M3+added_livingrooms_M4,                                           NA,added_kitchens_M2+added_kitchens_M3+added_kitchens_M4,                                    NA,added_storage_M2+added_storage_M3+added_storage_M4)##RED
to_plota_M3 = c(added_bedrooms_M2+added_bedrooms_M3,                                                      NA,added_livingrooms_M2+added_livingrooms_M3,                                                                NA,added_kitchens_M2+added_kitchens_M3,                                                      NA,added_storage_M2+added_storage_M3)##BLUE
to_plota_M2 = c(added_bedrooms_M2,                                                                        NA,added_livingrooms_M2,                                                                                     NA,added_kitchens_M2,                                                                        NA,added_storage_M2)##PURPLE




cols_A = rep(adegenet::transp("grey",c(0.1,0.4,0.7,0.9)),c(6,3,2,2))

barplot(to_plot_A+to_plota_M6,col=cols_A,lty=2,
        xlab="Rooms in compounds",xaxt="n",yaxt="n",
        ylab="Frequency", main = "Boane (October cohort)")
barplot(to_plot_A+to_plota_M5,add=TRUE,col = adegenet::transp("grey",0.2),
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
barplot(to_plot_A+to_plota_M4,add=TRUE,col = adegenet::transp("grey",0.2),
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
barplot(to_plot_A+to_plota_M3,add=TRUE,col = adegenet::transp("grey",0.2),
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
barplot(to_plot_A+to_plota_M2,add=TRUE,col = adegenet::transp("grey",0.2),
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
barplot(to_plot_A,add=TRUE,col = adegenet::transp("grey",0.2),
        xlab="",xaxt="n",yaxt="n",
        ylab="", main = "")


barplot(to_plot_M6,add=TRUE,col = adegenet::transp("yellow",0.7),
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
barplot(to_plot_M5,add=TRUE,col = adegenet::transp("orange",0.3),
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
barplot(to_plot_M4,add=TRUE,col = adegenet::transp("orange",0.3),
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
barplot(to_plot_M3,add=TRUE,col = adegenet::transp("orange"),
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
barplot(to_plot_M2,add=TRUE,col = adegenet::transp("darkred",0.7),
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
barplot(to_plot_M1,add=TRUE,col = "darkred",
        xlab="",xaxt="n",yaxt="n",border=NA,
        ylab="", main = "")
axis(1,at=seq(1,14,length=12),
     labels=c(1:5,NA,1:2,NA,1,NA,1))
axis(2,las=2, at=c(0,10,20,30,40,50,60))

abline(v=6.5,lty=2,lwd=2,col="grey20")
text(3.2,50,"Bedrooms")

abline(v=10.2,lty=2,lwd=2,col="grey20")
text(9.2,50,"Living rooms")

abline(v=13,lty=2,lwd=2,col="grey20")
text(11.2,50,"Kitchens")
text(14,50,"Storage rooms")

legend(2.6,90,
       legend = c("Added rooms (above solid line)",
                  "Modified rooms","M1 - M6 (Darker to paler shades)"),
       col=c("grey70","orange",NA),pch=15,bty="n",cex=1)

```


## Analysis 1

The impact of any indoor residual spraying (IRS) product will be time-dependent because the active ingredient wanes after application. A systematic review of experimental hut trial data (1) has previously assessed the entomological impacts of Actellic 300CS and SumiShield, the two IRS products used here. 

Results from the systematic review (1) for either Actellic 300®CS or SumiShield data are modified given the cone bioassay data reported in our study, weighted for the proportion of houses that are constructed with either mud or cement, to estimate the probable outcomes in Matutuine and Boane districts of southern Mozambique (Actellic 300®CS (main manuscript Fig. 2C & 2D), and SumiShield® (main manuscript Fig. 2E & 2F)) 


A bayesian logistic growth model is fitted to the mortality, successful feeding and deterrence data observed in a systematic review. We provide the RStan model code below (full_model.stan). We then fit the same function to the cone bioassay mortality data measured in our study (log_model.stan) when sampling either mud or cement surfaces. 

Data and simulated parameters for Analysis 1 - 3 are provided in Supplementary data

```{r, include = TRUE,  eval=FALSE}


## This is the model from the systematic review fitting to 
## mortality
## successful feeding
## deterrence

## full_model.stan
// bernoulli_logistic transformed data function
data {
  
  int<lower=1> N;                  // rows of data
  
  int<lower=0> n_t[N];             // Total number of mosquitoes entering IRS huts
  int<lower=0> d_t[N];             // Number mosquites dead sprayed hut
  int<lower=0> fed_t[N];           // Number of mosquitoes feeding in IRS HUTS assuming 
                                   // equal feeding for dead and alive ones
  int<lower=0> deterrence_IRS[N];  // Number of mosquitoes in sprayed huts
  int<lower=0> deterrence_total[N]; //Total number of mosquitoes in both sprayed and 
                                    //control huts
  
  vector<lower=0>[N] time;       // predictor

}

parameters {
  //Consider death. This is the proportion of mosquitoes dying (d_t) in treated huts 
  //(n_t)
  real alpha1;
  real alpha2;
  
  //Consider feeding. This is the proportion of mosquitoes that successfully fed  
  //in treatment (f_t)
  real beta1;
  real beta2;
  
  //Consider feeding. This is the proportion of mosquitoes that successfully fed 
  //in treatment (f_t)
  real omega1;
  real omega2;
  
  //  vector[N_study] study_a;
  //  real<lower=0,upper=10> sigma;
}

model {
  real sp[N];
  real fp[N];
  real det[N];
  
  alpha1 ~ normal(0,100);
  alpha2 ~ normal(0,100);
  
  beta1 ~ normal(0,100);
  beta2 ~ normal(0,100);
  
  omega1 ~ normal(0,100);
  omega2 ~ normal(0,100);
  
  //  study_a ~ normal(0,sigma);
  
  for (n in 1:N) {
    sp[n] = alpha1  + alpha2 * time[n];
    fp[n] = beta1  + beta2 * time[n];
    det[n] = omega1  + omega2 * time[n];
  }
  
  d_t ~ binomial_logit(n_t, sp);
  fed_t ~ binomial_logit(n_t, fp);
  deterrence_IRS ~ binomial_logit(deterrence_total, det);
}


## This is the model adjusted here to fit to 
## cone bioassay mortality in data from Southern Mozambique
## log_model.stan
// bernoulli_logistic transformed data function
data {
  
  int<lower=1> N;                  // rows of data
  
  int<lower=0> n_t[N];             // Total number of mosquitoes counted
  int<lower=0> d_t[N];             // Number mosquites killed during the test
  
  vector<lower=0>[N] time;         // time predictor e.g. months
  
  int<lower=1> N_eff;              // a random effect eg wall type / location / 
                                   // mosquito species etc
  int<lower=1, upper = N_eff> eff[N];
  
}

parameters {
  //Consider death. This is the proportion of mosquitoes dying (d_t) of 
  //all tested (n_t)
  real alpha1[N_eff];
  real alpha2[N_eff];
  
}

model {
  real sp[N];
  
  alpha1 ~ normal(0,10);
  alpha2 ~ normal(0,10);
  
  for (n in 1:N) {
    sp[n] = alpha1[eff[n]] + alpha2[eff[n]] * time[n];
  }
  
  d_t ~ binomial_logit(n_t, sp);
}

generated quantities{
  real sp_ppc[N_eff, 365];// this is to predict for 365 time points so 
                          // adjust time accordingly
    
    for(v in 1:N_eff){
      for(t in 1:365){
        sp_ppc[v, t] = binomial_rng(365, inv_logit(alpha1[v] + alpha2[v] * t)) / 365.0;
      }
    }
}


############################
##
## Estimating the probable outcome of a feeding attempt
##
############################

## Modelling the impact 
stan_Acte <- stan(file="models/probability_estimates_lq and kq_random_effect_mean.stan", 
                  data=act_dattest_base, ## Data from Sherrard-Smith et al (2018) (1)
                  warmup=1000,
                  control = list(adapt_delta = 0.8,
                                 max_treedepth = 20),
                  iter=2000, chains=4)


## Modelling the impact 
stan_Sumi <- stan(file="models/probability_estimates_lq and kq_random_effect_mean.stan", 
                  data=sum_dattest_base, ## Data from Sherrard-Smith et al (2018) (1)
                  warmup=1000,
                  control = list(adapt_delta = 0.8,
                                 max_treedepth = 20),
                  iter=2000, chains=4)


#library(shinystan)  ## can use this to check the model diagnostics
#launch_shinystan(stan_base)

base_Acte <- extract(stan_Acte)
base_Sumi <- extract(stan_Sumi)

time=seq(1,365,length=365)
mean_valssp_Acte  = 1 / (1 + exp(-mean(base_Acte$alpha1) - mean(base_Acte$alpha2)*time))
mean_valssp_ActeU = 1 / (1 + exp(-quantile(base_Acte$alpha1,0.9) - quantile(base_Acte$alpha2,0.9)*time))
mean_valssp_ActeL = 1 / (1 + exp(-quantile(base_Acte$alpha1,0.1) - quantile(base_Acte$alpha2,0.1)*time))

mean_valsfp_Acte  = (1 / (1 + exp(-mean(base_Acte$beta1) - mean(base_Acte$beta2)*time)))
mean_valsfp_ActeU = (1 / (1 + exp(-quantile(base_Acte$beta1,0.9) - quantile(base_Acte$beta2,0.9)*time)))
mean_valsfp_ActeL = (1 / (1 + exp(-quantile(base_Acte$beta1,0.1) - quantile(base_Acte$beta2,0.1)*time)))

##setting same depreciation as mortality for deterrence
mean_valsdet_Acte  = 1 / (1 + exp(-mean(base_Acte$omega1) - mean(base_Acte$alpha2)*time))
mean_valsdet_ActeU = 1 / (1 + exp(-quantile(base_Acte$omega1,0.9) - quantile(base_Acte$alpha2,0.9)*time))
mean_valsdet_ActeL = 1 / (1 + exp(-quantile(base_Acte$omega1,0.1) - quantile(base_Acte$alpha2,0.1)*time))


mean_valssp_Sumi  = 1 / (1 + exp(-mean(base_Sumi$alpha1) - mean(base_Sumi$alpha2)*time))
mean_valssp_SumiU = 1 / (1 + exp(-quantile(base_Sumi$alpha1,0.9) - quantile(base_Sumi$alpha2,0.9)*time))
mean_valssp_SumiL = 1 / (1 + exp(-quantile(base_Sumi$alpha1,0.1) - quantile(base_Sumi$alpha2,0.1)*time))

mean_valsfp_Sumi  = (1 / (1 + exp(-mean(base_Sumi$beta1) - mean(base_Sumi$beta2)*time)))
mean_valsfp_SumiU = (1 / (1 + exp(-quantile(base_Sumi$beta1,0.9) - quantile(base_Sumi$beta2,0.9)*time)))
mean_valsfp_SumiL = (1 / (1 + exp(-quantile(base_Sumi$beta1,0.1) - quantile(base_Sumi$beta2,0.1)*time)))

##setting same depreciation as mortality for deterrence
mean_valsdet_Sumi  = 1 / (1 + exp(-mean(base_Sumi$omega1) - mean(base_Sumi$alpha2)*time))
mean_valsdet_SumiU = 1 / (1 + exp(-quantile(base_Sumi$omega1,0.9) - quantile(base_Sumi$alpha2,0.9)*time))
mean_valsdet_SumiL = 1 / (1 + exp(-quantile(base_Sumi$omega1,0.1) - quantile(base_Sumi$alpha2,0.1)*time))


## Plotting these produces part of Figure 2 main manuscript

```

We then estimate the weighted-average mortality impact on mosquitoes given the ratio of mud vs cement walls in Matutuine or Boane.

These outcomes are then combined with the systematic review to give us a method to track the waning entomological impact (on mosquito mortality, successful blood-feeding and deterrence) of the spray products over time since a household was treated.

The results are shown in Figure 5 main manuscript.

```{r echo=TRUE,  eval=FALSE}
####################################################################
##
## 1 Cone bioassay data from the field 
##
#####################################################################

NEW_DAT = read.csv("data\\raw_data_2016_2017.csv",header=TRUE)
NEW_DAT$total_exposed = NEW_DAT$exposed_mosquito_1 + NEW_DAT$exposed_mosquito_2 + 
  NEW_DAT$exposed_mosquito_3 + NEW_DAT$exposed_mosquito_4 
NEW_DAT$total_mortality_24 = NEW_DAT$mortalidade_24h_1 + NEW_DAT$mortalidade_24h_2 + 
  NEW_DAT$mortalidade_24h_3 + NEW_DAT$mortalidade_24h_4
NEW_DAT$total_mortality_72 = NEW_DAT$mortalidade_72h_1 + NEW_DAT$mortalidade_72h_2 + 
  NEW_DAT$mortalidade_72h_3 + NEW_DAT$mortalidade_72h_4


NEW_DAT2 = data.frame(local = rep("Actellic_2016-2017-location",nrow(NEW_DAT)),
                      test_date = NEW_DAT$test_date,
                      month_official = NEW_DAT$Month,
                      house_type = NEW_DAT$house_type,
                      participation = NEW_DAT$participation,
                      mosquito_species = NEW_DAT$mosquito_species,
                      total_exposed = NEW_DAT$total_exposed,
                      total_mortality_24 = NEW_DAT$total_mortality_24,
                      total_mortality_72 = NEW_DAT$total_mortality_72)



Sumi_new_dat = read.csv("data\\raw_data_2018_2019_SumiShield (1).csv",header=TRUE)
Sumi_new_dat$total_exposed = Sumi_new_dat$exposed_mosquito_1 + 
  Sumi_new_dat$exposed_mosquito_2 + Sumi_new_dat$exposed_mosquito_3  
Sumi_new_dat$total_mortality_24 = Sumi_new_dat$mortalidade_24h_1 + 
  Sumi_new_dat$mortalidade_24h_2 + Sumi_new_dat$mortalidade_24h_3
Sumi_new_dat$total_mortality_72 = Sumi_new_dat$mortalidade_72h_1 + 
  Sumi_new_dat$mortalidade_72h_2 + Sumi_new_dat$mortalidade_72h_3
Sumi_new_dat$date_of_test = Sumi_new_dat$test_date


Sumi_new_dat = tidyr::separate(Sumi_new_dat, "test_date", c("Year", "Month", "Day"), sep = "-")

Sumi_new_dat2 = data.frame(local = rep("Sumi_2017-2018-location",nrow(Sumi_new_dat)),
                           test_date = Sumi_new_dat$date_of_test,
                           month_official = Sumi_new_dat$month_test,
                           house_type = Sumi_new_dat$house_type,
                           participation = Sumi_new_dat$participation,
                           mosquito_species = Sumi_new_dat$mosquito_species,
                           total_exposed = Sumi_new_dat$total_exposed,
                           total_mortality_24 = Sumi_new_dat$total_mortality_24,
                           total_mortality_72 = Sumi_new_dat$total_mortality_72)


## Decision is to use the 2016-2017 data for Actellic and then the 2017-2018 for Sumi 72 hours
cone_bios = rbind(Sumi_new_dat2, NEW_DAT2)

Con_bio_Acte_d_t_mud = 
  Con_bio_Acte_n_t_mud = 
  Con_bio_Sumi_d_t_mud = 
  Con_bio_Sumi_n_t_mud = 
  Con_bio_Acte_d_t_cem = 
  Con_bio_Acte_n_t_cem = 
  Con_bio_Sumi_d_t_cem = 
  Con_bio_Sumi_n_t_cem = numeric(length(unique(cone_bios$month_official)))

for(m in 1:length(unique(cone_bios$month_official))){
  Con_bio_Acte_d_t_mud[m] =  sum(cone_bios$total_mortality_24[cone_bios$house_type == "Mud" &
                                                                cone_bios$local == "Actellic_2016-2017-location" & cone_bios$month_official == unique(cone_bios$month_official)[m]])
  Con_bio_Acte_n_t_mud[m] =  sum(cone_bios$total_exposed[cone_bios$house_type == "Mud" &
                                                           cone_bios$local == "Actellic_2016-2017-location" &
                                                           cone_bios$month_official == unique(cone_bios$month_official)[m]])
  Con_bio_Sumi_d_t_mud[m] =  sum(cone_bios$total_mortality_72[cone_bios$house_type == "Mud" &
                                                                cone_bios$local == "Sumi_2017-2018-location" &
                                                                cone_bios$month_official == unique(cone_bios$month_official)[m]])
  Con_bio_Sumi_n_t_mud[m] =  sum(cone_bios$total_exposed[cone_bios$house_type == "Mud" &
                                                           cone_bios$local == "Sumi_2017-2018-location" &
                                                           cone_bios$month_official == unique(cone_bios$month_official)[m]])
  
  Con_bio_Acte_d_t_cem[m] =  sum(cone_bios$total_mortality_24[cone_bios$house_type == "Cement" & cone_bios$local == "Actellic_2016-2017-location" & cone_bios$month_official == unique(cone_bios$month_official)[m]])
  Con_bio_Acte_n_t_cem[m] =  sum(cone_bios$total_exposed[cone_bios$house_type == "Cement" & cone_bios$local == "Actellic_2016-2017-location" & cone_bios$month_official == unique(cone_bios$month_official)[m]])
  Con_bio_Sumi_d_t_cem[m] =  sum(cone_bios$total_mortality_72[cone_bios$house_type == "Cement" & cone_bios$local == "Sumi_2017-2018-location" & cone_bios$month_official == unique(cone_bios$month_official)[m]])
  Con_bio_Sumi_n_t_cem[m] =  sum(cone_bios$total_exposed[cone_bios$house_type == "Cement" &
                                                           cone_bios$local == "Sumi_2017-2018-location" &
                                                           cone_bios$month_official == unique(cone_bios$month_official)[m]])
}


  ## Add in a line to demonstrate the residual efficacy estimated by Mercy in MOZAMBIQUE
  data_list_mud = list(N = N_data, ## number
                   d_t = Con_bio_d_t_mud,## repeat for each chemistry
                   n_t = Con_bio_n_t_mud,
                   time = time_sequence,
                   N_eff = 1, ## eg '2' for 2 wall types
                   eff = rep(1,N_data))##[the number of reps for each group in your data]
  
  data_list_cem = list(N = N_data, ## number
                       d_t = Con_bio_d_t_cem,
                       n_t = Con_bio_n_t_cem,
                       time = time_sequence,
                       N_eff = 1, ## eg '2' for 2 wall types
                       eff = rep(1,N_data))##[the number of reps for each group in your data]
  
  
  stan_model_mud <- stan(file="models/log_mod.stan", 
                     data=data_list_mud, 
                     warmup=500,
                     control = list(adapt_delta = 0.9,
                                    max_treedepth = 20),
                     iter=1000, chains=4)
  
  stan_model_cem <- stan(file="models/log_mod.stan", 
                         data=data_list_cem, 
                         warmup=500,
                         control = list(adapt_delta = 0.9,
                                        max_treedepth = 20),
                         iter=1000, chains=4)

  base_moz1 <- extract(stan_model_mud) ## can use this to extract the model parameter estimates
  base_moz2 <- extract(stan_model_cem) ## can use this to extract the model parameter estimates
  
  ## plot it against your data!
  d_t1 = Con_bio_d_t_mud
  n_t1 = Con_bio_n_t_mud
  DEAD1 = d_t1/n_t1
  
  d_t2 = Con_bio_d_t_cem
  n_t2 = Con_bio_n_t_cem
  DEAD2 = d_t2/n_t2

  time = seq(1,365,by=1)
  
  mean_prediction_mud = 1 / (1 + exp(-mean(base_moz1$alpha1[,1]) - 
                                       mean(base_moz1$alpha2[,1])*time))
  max_prediction_mud = 1 / (1 + exp(-quantile(base_moz1$alpha1[,1],0.9) - 
                                      quantile(base_moz1$alpha2[,1],0.9)*time))
  min_prediction_mud = 1 / (1 + exp(-quantile(base_moz1$alpha1[,1],0.1) - 
                                      quantile(base_moz1$alpha2[,1],0.1)*time))
  
  mean_prediction_cem = 1 / (1 + exp(-mean(base_moz2$alpha1[,1]) - 
                                       mean(base_moz2$alpha2[,1])*time))
  max_prediction_cem = 1 / (1 + exp(-quantile(base_moz2$alpha1[,1],0.9) - 
                                      quantile(base_moz2$alpha2[,1],0.9)*time))
  min_prediction_cem = 1 / (1 + exp(-quantile(base_moz2$alpha1[,1],0.1) - 
                                      quantile(base_moz2$alpha2[,1],0.1)*time))
  
  ## Plotting these produces part of Figure 2 main manuscript

  
  ## The mean prediction is weighted by the proportion of households
  ## with mud or cement walls in each village
  
  ## percent_mud: 40% for Matutuine, 97% for Boane
  ## percent_cem: 60% for Matutuine,  3% for Boane
  mean_prediction = (mean_prediction_mud*percent_mud) + (mean_prediction_cem*percent_cem)
  
  feed2 = (1 - mean_prediction) * mean_valsfp_checker4 * (1 - mean_valsdet_checker4)
  death2 = mean_prediction  * (1 - mean_valsdet_checker4)
  rep2 = (1 - (death1 + feed1)) * (1 - mean_valsdet_checker4)
  deter2 = mean_valsdet_checker4  
  
  TOTS2 = feed2 + rep2 + death2 + deter2
  
  ##e.g for Matuttuine
  PERCENT_MUD = 0.40
  PERCENT_CEM = 0.60

percent_mud = PERCENT_MUD
percent_cem = PERCENT_CEM

mean_prediction = (mean_prediction_mud*percent_mud) + (mean_prediction_cem*percent_cem)
max_prediction = (max_prediction_mud*percent_mud) + (max_prediction_cem*percent_cem)
min_prediction = (min_prediction_mud*percent_mud) + (min_prediction_cem*percent_cem)

feed2 = (1 - mean_prediction) * mean_valsfp_Acte * (1 - mean_valsdet_Acte)
death2 = mean_prediction  * (1 - mean_valsdet_Acte)


feed2l = (1 - min_prediction) * mean_valsfp_ActeL * (1 - mean_valsdet_ActeL)
death2l = min_prediction  * (1 - mean_valsdet_ActeL)
feed2u = (1 - max_prediction) * mean_valsfp_ActeU * (1 - mean_valsdet_ActeU)
death2u = max_prediction  * (1 - mean_valsdet_ActeU)

## This is repeated for Boane and Sumishield data and combined into a data file

dta1 = data.frame(
  time = time,
  acte_death2 = death2,
  acte_death2u = death2u,
  acte_death2l = death2l,
  acte_fed2 = feed2,
  acte_fed2l = feed2l,
  acte_fed2u = feed2u,
  
  sumi_death2 = death2s,
  sumi_death2u = death2us,
  sumi_death2l = death2ls,
  sumi_fed2 = feed2s,
  sumi_fed2l = feed2ls,
  sumi_fed2u = feed2us
  )



```


## Analysis 2

The time-dependent efficacy from LLINs is estimated similarly following (2). The successful biting (s_ITN), repeating (r_ITN), and killing (d_ITN) in the presence of LLINs also wanes with time as determined from systematic review of experimental hut data testing unwashed and washed pyrethroid treated mosquito nets (ITNs). We assume the performance of ITNs will be equivalent to nets aged 1.5 years as the mass campaign took place in 2016 - 2017 in Southern Mozambique. 

```{r echo = TRUE, eval = FALSE}

##############################
##
## 2 Estimated impact of ITNs, from Churcher et al. 2016 (2)
##
###############################


## The following parameters are taken from (Churcher et al 2016 (2))		
##
itn_half_life = 2.64

d_ITN0 <- 0.51
s_ITN0 <- 0.31
r_ITN0 <- 1-ERG_d_ITN0-ERG_s_ITN0

itn_loss = log(2)/itn_half_life

ITN_interval=3*365


## decay in efficacy of net over time
#time=1:(365*3)
ITN_decay = exp(-(time/ITN_interval)*itn_loss)

r_ITN_min=0.24 
d_ITN = ERG_d_ITN0 * ITN_decay 	 		## insecticide mortality rate 
r_ITN = r_ITN_min + (ERG_r_ITN0 - r_ITN_min)*ITN_decay 
s_ITN = 1 - d_ITN - r_ITN			## successful protected human biting 



```


## Analysis 3


To quantify the impact of post-spray wall modification, prolonged spray campaigns, and IRS efficacy on IRS effectiveness, we adapt a mechanistic vector model approach determined in Le Menach 2007 (3) and Griffin et al (2010) (4) and updated in Walker et al 2016 (5). This model outlines how indoor interventions are affecting the number of mosquito bites received per person per time unit which has ramifications for the infectious mosquito bites received per person per year (the entomological inoculation rate, EIR) and malaria transmission. The probability that a blood-seeking mosquito successfully feeds will depend on the species-specific bionomics and behaviors of the mosquito (e.g. the proportion of bites taken on humans, the proportion of bites received indoors or in bed) and the vector interventions that protect the human population. 

In our case, in the absence of locally available mosquito bionomics data, we use a sensitivity analyis ranging estimates for the probability of a mosquito biting indoors from 0.68 to 0.99, and a mosquito biting in bed from 0.6 to 0.95 following ranges observed in Sherrard-Smith et al (2019) (6) for these parameters. These estimates are coupled with the 80% uncertainty intervals from the posterior draws for the estimation of efficacy of IRS in Analysis 1 above. 


```{r echo = TRUE, eval = FALSE}

## These are the Bayesian posterior draws for IRS impact
actellic_details = dta1[,1:7]
sumishield_details = dta1[,c(1,8:13)]


## We investigate impacts as per

##  1 the effect if there is no intervention
##  2 with ITNs only
##  3 with IRS only no loss in coverage
##  4 with IRS only loss in coverage

## And repeat for loss in coverage

## Figure 6 main manuscript
par(mfrow = c(2,3))


w_Acte = yy_Acte = z_Acte = w_Sumi = yy_Sumi = z_Sumi = array(dim=c(180,4,9)) 
## row = time series
## col 1 = no intervention
## col 2 = nets only
## col 3 = spray only
## col 4 = both nets and spray
## dimension 3 stores the uncertainty from phi parameter and efficacy estimates

#############################
## 

##sensitivity analysis
##Species are different in each location 

# use PNAS paper to estimate some range for
# the values of phi B and I (ref 6 below)

PHI_B_mut = c(0.85,0.6,0.95) ## probability of bites in bed (mean, lower and upper)
PHI_I_mut = c(0.90,0.68,0.99) ## probability of bites indoors

PHI_B_boa = c(0.85,0.6,0.95)  ## probability of bites in bed
PHI_I_boa = c(0.90,0.68,0.99) ## probability of bites indoors

## From Griffin et al 2010 (4)
k0 = 0.699 ## expected feeding in the absence of interventions
ksA = actellic_details[,5]
lsA = actellic_details[,2]
jsA = 1 - actellic_details[,2] - actellic_details[,5]

s_IRS_Acte = ksA/k0 ##feed2
r_IRS_Acte = (1 - ksA/k0)*(jsA/(lsA+jsA)) ##rep2

ksS = sumishield_details[,5]
lsS = sumishield_details[,2]
jsS = 1 - sumishield_details[,2] - sumishield_details[,5]

s_IRS_Sumi = ksS/k0 ##feed2
r_IRS_Sumi = (1 - ksS/k0)*(jsS/(lsS+jsS)) ##rep2

## lower
ksAl = actellic_details[,6]
lsAl = actellic_details[,3]
jsAl = 1 - actellic_details[,6] - actellic_details[,3]

s_IRS_Actel = ksAl/k0 ##feed2
r_IRS_Actel = (1 - ksAl/k0)*(jsAl/(lsAl+jsAl)) ##rep2

ksSl = sumishield_details[,6]
lsSl = sumishield_details[,3]
jsSl = 1 - sumishield_details[,6] - sumishield_details[,3]

s_IRS_Sumil = ksSl/k0 ##feed2
r_IRS_Sumil = (1 - ksSl/k0)*(jsSl/(lsSl+jsSl)) ##rep2

## upper
ksAu = actellic_details[,7]
lsAu = actellic_details[,4]
jsAu = 1 - actellic_details[,7] - actellic_details[,4]

s_IRS_Acteu = ksAu/k0 ##feed2
r_IRS_Acteu = (1 - ksAu/k0)*(jsAu/(lsAu+jsAu)) ##rep2

ksSu = sumishield_details[,7]
lsSu = sumishield_details[,4]
jsSu = 1 - sumishield_details[,7] - sumishield_details[,4]

s_IRS_Sumiu = ksSu/k0 ##feed2
r_IRS_Sumiu = (1 - ksSu/k0)*(jsSu/(lsSu+jsSu)) ##rep2

##
w_Acte[,1,] = w_Sumi[,1,] = rep(1,180) 
## Probability that a mosquito bites and survives in the presence of indoor vector control

cl = c(0,3,6)
for(j in 1:3){
  for(i in 1:180){
    PHI_B = PHI_B_mut[j]
    PHI_I = PHI_I_mut[j]
    w_Acte[i,2,1+cl[j]] = 1 - PHI_B + PHI_B*s_ITN[i+547]				 
    ## probability of surviving biting given that there is ITN
    w_Acte[i,3,1+cl[j]] = 1 - PHI_I + PHI_I*(1-r_IRS_Acte[i])*s_IRS_Acte[i]	
    ##			probability of surviving biting given that there is IRS
    w_Acte[i,4,1+cl[j]] = 1 - PHI_I + PHI_B*(1-r_IRS_Acte[i])*s_ITN[i+547]*s_IRS_Acte[i] + (PHI_I - PHI_B)*(1-r_IRS_Acte[i])*s_IRS_Acte[i] ## probability of surviving biting given that there is ITN & IRS
    
    w_Acte[i,2,2+cl[j]] = 1 - PHI_B + PHI_B*s_ITN[i+547]				 
    ## probability of surviving biting given that there is ITN
    w_Acte[i,3,2+cl[j]] = 1 - PHI_I + PHI_I*(1-r_IRS_Actel[i])*s_IRS_Actel[i]	
    ##			probability of surviving biting given that there is IRS
    w_Acte[i,4,2+cl[j]] = 1 - PHI_I + PHI_B*(1-r_IRS_Actel[i])*s_ITN[i+547]*s_IRS_Actel[i] + (PHI_I - PHI_B)*(1-r_IRS_Actel[i])*s_IRS_Actel[i] ## probability of surviving biting given that there is ITN & IRS
    
    w_Acte[i,2,3+cl[j]] = 1 - PHI_B + PHI_B*s_ITN[i+547]				 
    ## probability of surviving biting given that there is ITN
    w_Acte[i,3,3+cl[j]] = 1 - PHI_I + PHI_I*(1-r_IRS_Acteu[i])*s_IRS_Acteu[i]	
    ##			probability of surviving biting given that there is IRS
    w_Acte[i,4,3+cl[j]] = 1 - PHI_I + PHI_B*(1-r_IRS_Acteu[i])*s_ITN[i+547]*s_IRS_Acteu[i] + (PHI_I - PHI_B)*(1-r_IRS_Acteu[i])*s_IRS_Acteu[i] ## probability of surviving biting given that there is ITN & IRS
  }  
}

cl = c(0,3,6) ## to capture the ranging uncertainty estimates
for(j in 1:3){
  for(i in 1:180){
    PHI_B = PHI_B_mut[j]
    PHI_I = PHI_I_mut[j]
    
  w_Sumi[i,2,1+cl[j]] = 1 - PHI_B + PHI_B*s_ITN[i+547]				 
  ## probability of surviving biting given that there is ITN
  w_Sumi[i,3,1+cl[j]] = 1 - PHI_I + PHI_I*(1-r_IRS_Sumi[i])*s_IRS_Sumi[i]	
  ##			probability of surviving biting given that there is IRS
  w_Sumi[i,4,1+cl[j]] = 1 - PHI_I + PHI_B*(1-r_IRS_Sumi[i])*s_ITN[i+547]*s_IRS_Sumi[i] + 
    (PHI_I - PHI_B)*(1-r_IRS_Sumi[i])*s_IRS_Sumi[i] 
  ## probability of surviving biting given that there is ITN & IRS

  w_Sumi[i,2,2+cl[j]] = 1 - PHI_B + PHI_B*s_ITN[i+547]				 
  ## probability of surviving biting given that there is ITN
  w_Sumi[i,3,2+cl[j]] = 1 - PHI_I + PHI_I*(1-r_IRS_Sumil[i])*s_IRS_Sumil[i]	
  ##			probability of surviving biting given that there is IRS
  w_Sumi[i,4,2+cl[j]] = 1 - PHI_I + PHI_B*(1-r_IRS_Sumil[i])*s_ITN[i+547]*s_IRS_Sumil[i] + 
    (PHI_I - PHI_B)*(1-r_IRS_Sumil[i])*s_IRS_Sumil[i] 
  ## probability of surviving biting given that there is ITN & IRS

  w_Sumi[i,2,3+cl[j]] = 1 - PHI_B + PHI_B*s_ITN[i+547]				 
  ## probability of surviving biting given that there is ITN
  w_Sumi[i,3,3+cl[j]] = 1 - PHI_I + PHI_I*(1-r_IRS_Sumiu[i])*s_IRS_Sumiu[i]	
  ##			probability of surviving biting given that there is IRS
  w_Sumi[i,4,3+cl[j]] = 1 - PHI_I + PHI_B*(1-r_IRS_Sumiu[i])*s_ITN[i+547]*s_IRS_Sumiu[i] + 
    (PHI_I - PHI_B)*(1-r_IRS_Sumiu[i])*s_IRS_Sumiu[i] 
  ## probability of surviving biting given that there is ITN & IRS
  }
}


## Probability of any bite (if there is IRS, a mosquito may bite and then die immediately afterwards)
yy_Acte[,1,] = w_Acte[,1,] 
yy_Acte[,2,] = w_Acte[,2,]

yy_Sumi[,1,] = w_Sumi[,1,] 
yy_Sumi[,2,] = w_Sumi[,2,]

for(j in 1:3){
  for(i in 1:180){
  PHI_B = PHI_B_mut[j]
  PHI_I = PHI_I_mut[j]
  yy_Acte[i,3,1+cl[j]] = 1 - PHI_I + PHI_I*(1-r_IRS_Acte[i])
  yy_Acte[i,4,1+cl[j]] = 1 - PHI_I + PHI_B*(1-r_IRS_Acte[i])*s_ITN[i+547] + 
    (PHI_I - PHI_B)*(1-r_IRS_Acte[i])

  yy_Acte[i,3,2+cl[j]] = 1 - PHI_I + PHI_I*(1-r_IRS_Actel[i])
  yy_Acte[i,4,2+cl[j]] = 1 - PHI_I + PHI_B*(1-r_IRS_Actel[i])*s_ITN[i+547] + 
    (PHI_I - PHI_B)*(1-r_IRS_Actel[i])

  yy_Acte[i,3,3+cl[j]] = 1 - PHI_I + PHI_I*(1-r_IRS_Acteu[i])
  yy_Acte[i,4,3+cl[j]] = 1 - PHI_I + PHI_B*(1-r_IRS_Acteu[i])*s_ITN[i+547] + 
    (PHI_I - PHI_B)*(1-r_IRS_Acteu[i])
  }
}

for(j in 1:3){
  for(i in 1:180){
    PHI_B = PHI_B_boa[j]
    PHI_I = PHI_I_boa[j]
    yy_Sumi[i,3,1+cl[j]] = 1 - PHI_I + PHI_I*(1-r_IRS_Sumi[i])
    yy_Sumi[i,4,1+cl[j]] = 1 - PHI_I + PHI_B*(1-r_IRS_Sumi[i])*s_ITN[i+547] + 
      (PHI_I - PHI_B)*(1-r_IRS_Sumi[i])
    
    yy_Sumi[i,3,2+cl[j]] = 1 - PHI_I + PHI_I*(1-r_IRS_Sumil[i])
    yy_Sumi[i,4,2+cl[j]] = 1 - PHI_I + PHI_B*(1-r_IRS_Sumil[i])*s_ITN[i+547] + 
      (PHI_I - PHI_B)*(1-r_IRS_Sumil[i])
    
    yy_Sumi[i,3,3+cl[j]] = 1 - PHI_I + PHI_I*(1-r_IRS_Sumiu[i])
    yy_Sumi[i,4,3+cl[j]] = 1 - PHI_I + PHI_B*(1-r_IRS_Sumiu[i])*s_ITN[i+547] + 
      (PHI_I - PHI_B)*(1-r_IRS_Sumiu[i])
  }  
}

## 
plot(yy_Acte[,1,1] ~ time[1:180],ylim=c(0,1),pch="",
     ylab = "Probability mosquito bites",
     col="black",
     main = "",cex.main=1.2,xlim=c(-60,180),xaxt="n",
     xlab="Time in months",yaxt="n",cex.lab=1.4,cex.axis=1.4,cex=1.4)
axis(2,las=2,at=seq(0,1,0.2),labels=seq(0,1,0.2),cex.lab=1.4,cex.axis=1.4)
axis(1,at=seq(-60,150,30)+15,labels = c("Sep","Oct","Nov","Dec","Jan","Feb","Mar","Apr"),
     cex.axis = 1.4)

colsd=c("darkred","red","orange","blue")
  for(i in 3){
    lines(yy_Acte[,i,1] ~ time[1:180],col="darkblue",lwd=2)
    lines(yy_Sumi[,i,1] ~ time[1:180],col="aquamarine3",lwd=2)
  }


## Including max uncertainty for phiI, phiB and efficacy
polygon(c(time[1:180],rev(time[1:180])),
        c(yy_Acte[,3,5],rev(yy_Acte[,3,9])),
        col=adegenet::transp("darkblue",0.3),border=NA)
polygon(c(time[1:180],rev(time[1:180])),
        c(yy_Sumi[,3,5],rev(yy_Sumi[,3,9])),
        col=adegenet::transp("aquamarine3",0.3),border=NA)

legend("topleft",legend = c("Actellic 300CS","SumiShield"),
       col = c("darkblue","aquamarine3"),lwd = 2, lty=c(1,1),cex=1.2,bty="n")


## 
plot(w_Acte[,1,1] ~ time[1:180],ylim=c(0,1),pch="",
     ylab = "Probability mosquito bites and survives",
     col="black",
     main = "",cex.main=1.2,xlim=c(-60,180),xaxt="n",
     xlab="Time in months",yaxt="n",cex.lab=1.4,cex.axis=1.4,cex=1.4)
axis(2,las=2,at=seq(0,1,0.2),labels=seq(0,1,0.2),cex.lab=1.4,cex.axis=1.4)
axis(1,at=seq(-60,150,30)+15,labels = c("Sep","Oct","Nov","Dec","Jan","Feb","Mar","Apr"),
     cex.axis = 1.4)

colsd=c("darkred","red","orange","blue")
for(i in 3){
  lines(w_Acte[,i,1] ~ time[1:180],col="darkblue",lwd = 2)
  lines(w_Sumi[,i,1] ~ time[1:180],col="aquamarine3",lwd = 2)
}
polygon(c(time[1:180],rev(time[1:180])),
        c(w_Acte[,3,5],rev(w_Acte[,3,9])),
        col=adegenet::transp("darkblue",0.3),border=NA)
polygon(c(time[1:180],rev(time[1:180])),
        c(w_Sumi[,3,5],rev(w_Sumi[,3,9])),
        col=adegenet::transp("aquamarine3",0.3),border=NA)


## Probability repelled
z_Acte[,1,1] = 0
z_Sumi[,1,1] = 0

for(j in 1:3){
  for(i in 1:180){
    PHI_B = PHI_B_boa[j]
    PHI_I = PHI_I_boa[j]

  z_Acte[i,2,1+cl[j]] = PHI_B*r_ITN[i+547]
  z_Acte[i,3,1+cl[j]] = PHI_I*r_IRS_Acte[i]
  z_Acte[i,4,1+cl[j]] = PHI_B*(r_IRS_Acte[i] + (1-r_IRS_Acte[i])*r_ITN[i+547]) + (PHI_I - PHI_B)*r_IRS_Acte[i]

  z_Acte[i,2,2+cl[j]] = PHI_B*r_ITN[i+547]
  z_Acte[i,3,2+cl[j]] = PHI_I*r_IRS_Actel[i]
  z_Acte[i,4,2+cl[j]] = PHI_B*(r_IRS_Actel[i] + (1-r_IRS_Actel[i])*r_ITN[i+547]) + 
    (PHI_I - PHI_B)*r_IRS_Actel[i]

  z_Acte[i,2,3+cl[j]] = PHI_B*r_ITN[i+547]
  z_Acte[i,3,3+cl[j]] = PHI_I*r_IRS_Acteu[i]
  z_Acte[i,4,3+cl[j]] = PHI_B*(r_IRS_Acteu[i] + (1-r_IRS_Acteu[i])*r_ITN[i+547]) + 
    (PHI_I - PHI_B)*r_IRS_Acteu[i]
  
  z_Sumi[i,2,1+cl[j]] = PHI_B*r_ITN[i+547]
  z_Sumi[i,3,1+cl[j]] = PHI_I*r_IRS_Sumi[i]
  z_Sumi[i,4,1+cl[j]] = PHI_B*(r_IRS_Sumi[i] + (1-r_IRS_Sumi[i])*r_ITN[i+547]) + 
    (PHI_I - PHI_B)*r_IRS_Sumi[i]

  z_Sumi[i,2,2+cl[j]] = PHI_B*r_ITN[i+547]
  z_Sumi[i,3,2+cl[j]] = PHI_I*r_IRS_Sumil[i]
  z_Sumi[i,4,2+cl[j]] = PHI_B*(r_IRS_Sumil[i] + (1-r_IRS_Sumil[i])*r_ITN[i+547]) + 
    (PHI_I - PHI_B)*r_IRS_Sumil[i]

  z_Sumi[i,2,3+cl[j]] = PHI_B*r_ITN[i+547]
  z_Sumi[i,3,3+cl[j]] = PHI_I*r_IRS_Sumiu[i]
  z_Sumi[i,4,3+cl[j]] = PHI_B*(r_IRS_Sumiu[i] + (1-r_IRS_Sumiu[i])*r_ITN[i+547]) + 
    (PHI_I - PHI_B)*r_IRS_Sumiu[i]
  }
}
## 
plot(z_Acte[,1,1] ~ time[1:180],ylim=c(0,1),pch="",
     ylab = "Probability mosquito is repelled",
     col="black",
     main = "",cex.main=1.2,xlim=c(-60,180),xaxt="n",
     xlab="Time in months",yaxt="n",cex.lab=1.4,cex.axis=1.4,cex=1.4)
axis(2,las=2,at=seq(0,1,0.2),labels=seq(0,1,0.2),cex.lab=1.4,cex.axis=1.4)
axis(1,at=seq(-60,150,30)+15,labels = c("Sep","Oct","Nov","Dec","Jan","Feb","Mar","Apr"),
     cex.axis = 1.4)

colsd=c("darkred","red","orange","blue")
for(i in 3){
  lines(z_Acte[,i,1] ~ time[1:180],col="darkblue",lwd=2)
  lines(z_Sumi[,i,1] ~ time[1:180],col="aquamarine3",lwd=2)
}

polygon(c(time[1:180],rev(time[1:180])),
        c(z_Acte[,3,5],rev(z_Acte[,3,9])),
        col=adegenet::transp("darkblue",0.3),border=NA)
polygon(c(time[1:180],rev(time[1:180])),
        c(z_Sumi[,3,5],rev(z_Sumi[,3,9])),
        col=adegenet::transp("aquamarine3",0.3),border=NA)

## Campaigns tend to take up to a few months to complete
## We assume the ratio of houses monitored per start month
## reflects the proportion of houses covered by the spray campaign
## in that month

## Houses were tracked from November, December and January (1 in Feb)
## 129/(129+88+27+1) is 52.65% of houses in the community have max protection in Nov
## 88/(129+88+27+1) is 35.92% of houses max protection Dec (52% - any modifications have 1 mont old protection)
## 27/(129+88+27+1) is 11.02% max protection Jan (35.92% - modif 1 month old, 52% - modif 2 month old)


## derived ITN/IRS quantities
## prob bites and survives

w_Acte1 = yy_Acte1 = z_Acte1 = w_Sumi1 = yy_Sumi1 = z_Sumi1 = array(dim=c(365,18,4,9))
## row = time series
## cols indicate the ranging initiation of the spray campaign to be combined
## dimension 3: 1 will be the effect if there is no intervention
## dimension 3: is with ITNs only
## dimension 3: is with IRS only no loss in coverage
## dimension 3: is with IRS only loss in coverage
## dimensions 4: the uncertainty for efficacy and phi I, B

#############################
## 

## Data from spray campaign
prop_houses_sprayed_WeeklyB = 0.97*c(0,	0.027219794,	## August
                                0.077014558,	0.136261919,	0.196901742,	0.250817066, ## Sept
                                0.301047746,	0.347687015,	0.395348206,	0.464541108, ## Oct
                                0.521818166,	0.581372602,	0.643327061,	0.710948828, ## Nov
                                0.777620537,	0.847130239,	0.911498024,	0.930365931, ## Dec
                                0.947042313,	0.96389906,	0.983400068,	0.991357264,	 ## Jan
                                0.99238783,	1) ## Feb
prop_houses_sprayed_WeeklyM = 0.96*c(0.065358837,	0.193716785,## August
                                0.334444596,	0.432141444,	0.533708885,	0.614060416,##sep
                                0.667531537,	0.711462198,	0.769981823,	0.880751007,##oct
                                0.919045204,	0.944027976,	0.97443187,	0.990922736,  ##nov
                                0.991873307,	0.99744169,	 1,             1,          ##dec
                                1,        1) ## jan

ksA = lsA = jsA = array(dim=c(365,18,9))
for(w in 1:17){
  ksA[,1,1] =  actellic_details[,5][1:365]
  ksA[,w+1,1] = c(rep(k0,w*7),actellic_details[,5][1:(365-7*w)])

  ksA[,1,2] =  actellic_details[,6][1:365]
  ksA[,w+1,2] = c(rep(k0,w*7),actellic_details[,6][1:(365-7*w)])

  ksA[,1,3] =  actellic_details[,7][1:365]
  ksA[,w+1,3] = c(rep(k0,w*7),actellic_details[,7][1:(365-7*w)])
  
  
  lsA[,1,1] = actellic_details[,2]
  lsA[,w+1,1] = c(rep(0,w*7),actellic_details[,2][1:(365-7*w)])

  lsA[,1,2] = actellic_details[,3]
  lsA[,w+1,2] = c(rep(0,w*7),actellic_details[,3][1:(365-7*w)])
  
  lsA[,1,3] = actellic_details[,4]
  lsA[,w+1,3] = c(rep(0,w*7),actellic_details[,4][1:(365-7*w)])
  
  
  jsA[,w,1] = 1 - ksA[,w,1] - lsA[,w,1]
  jsA[,w,2] = 1 - ksA[,w,2] - lsA[,w,2]
  jsA[,w,3] = 1 - ksA[,w,3] - lsA[,w,3]
  
}
ksA[,,4:6] = ksA[,,1:3]
ksA[,,7:9] = ksA[,,1:3]

lsA[,,4:6] = lsA[,,1:3]
lsA[,,7:9] = lsA[,,1:3]

jsA[,,4:6] = jsA[,,1:3]
jsA[,,7:9] = jsA[,,1:3]

jsA[,18,] = 1 - ksA[,18,] - lsA[,18,]



s_IRS_Acte1 = r_IRS_Acte1 = array(dim=c(365,18,9))
for(j in 1:9){
  for(w in 1:18){
    s_IRS_Acte1[,w,j] = ksA[,w,j]/k0 ##feed2 = when IRS is implemented in month 1 (Nov)
    r_IRS_Acte1[,w,j] = (1 - ksA[,w,j]/k0)*(jsA[,w,j]/(lsA[,w,j]+jsA[,w,j])) ##rep2 

  }
  
}



ksS = lsS = jsS = array(dim=c(365,18,9))
for(w in 1:17){
  ksS[,1,1] =  sumishield_details[,5][1:365]
  ksS[,w+1,1] = c(rep(k0,w*7),sumishield_details[,5][1:(365-7*w)])
  
  ksS[,1,2] =  sumishield_details[,6][1:365]
  ksS[,w+1,2] = c(rep(k0,w*7),sumishield_details[,6][1:(365-7*w)])

  ksS[,1,3] =  sumishield_details[,7][1:365]
  ksS[,w+1,3] = c(rep(k0,w*7),sumishield_details[,7][1:(365-7*w)])

  
  lsS[,1,1] = sumishield_details[,2]
  lsS[,w+1,1] = c(rep(0,w*7),sumishield_details[,2][1:(365-7*w)])
  
  lsS[,1,2] = sumishield_details[,3]
  lsS[,w+1,2] = c(rep(0,w*7),sumishield_details[,3][1:(365-7*w)])

  lsS[,1,3] = sumishield_details[,4]
  lsS[,w+1,3] = c(rep(0,w*7),sumishield_details[,4][1:(365-7*w)])

  
  jsS[,w,1] = 1 - ksS[,w,1] - lsS[,w,1]
  jsS[,w,2] = 1 - ksS[,w,2] - lsS[,w,2]
  jsS[,w,3] = 1 - ksS[,w,3] - lsS[,w,3]
  
}
ksS[,,4:6] = ksS[,,1:3]
ksS[,,7:9] = ksS[,,1:3]

lsS[,,4:6] = lsS[,,1:3]
lsS[,,7:9] = lsS[,,1:3]

jsS[,,4:6] = jsS[,,1:3]
jsS[,,7:9] = jsS[,,1:3]

jsS[,18,] = 1 - ksS[,18,] - lsS[,18,]


s_IRS_Sumi1 = r_IRS_Sumi1 = array(dim=c(365,18,9))
for(j in 1:9){
  for(w in 1:18){
  s_IRS_Sumi1[,w,j] = ksS[,w,j]/k0 ##feed2 = when IRS is implemented in month 1 (Nov)
  r_IRS_Sumi1[,w,j] = (1 - ksS[,w,j]/k0)*(jsS[,w,j]/(lsS[,w,j]+jsS[,w,j])) ##rep2 
  }
}


w_Acte1[,,1,] = w_Sumi1[,,1,] = rep(1,365) 
## Probability that a mosquito bites and survives in the presence of indoor vector control
for(k in 1:3){
  for(j in 1:18){
    for(i in 1:365){
      PHI_B = PHI_B_mut[k]
      PHI_I = PHI_I_mut[k]
      w_Acte1[i,j,2,1+cl[k]] = 1 - PHI_B + PHI_B*s_ITN[i+547]				 
      ## probability of surviving biting given that there is ITN
      w_Acte1[i,j,3,1+cl[k]] = 1 - PHI_I + PHI_I*(1-r_IRS_Acte1[i,j,1])*s_IRS_Acte1[i,j,1]	
      ##			probability of surviving biting given that there is IRS
      w_Acte1[i,j,4,1+cl[k]] = 1 - PHI_I + PHI_B*(1-r_IRS_Acte1[i,j,1])*s_ITN[i+547]*s_IRS_Acte1[i,j,1] + 
        (PHI_I - PHI_B)*(1-r_IRS_Acte1[i,j,1])*s_IRS_Acte1[i,j,1] 
      ## probability of surviving biting given that there is ITN & IRS
      
      w_Sumi1[i,j,2,1+cl[k]] = 1 - PHI_B + PHI_B*s_ITN[i+547]				 
      ## probability of surviving biting given that there is ITN
      w_Sumi1[i,j,3,1+cl[k]] = 1 - PHI_I + PHI_I*(1-r_IRS_Sumi1[i,j,1])*s_IRS_Sumi1[i,j,1]	
      ##			probability of surviving biting given that there is IRS
      w_Sumi1[i,j,4,1+cl[k]] = 1 - PHI_I + PHI_B*(1-r_IRS_Sumi1[i,j,1])*s_ITN[i+547]*s_IRS_Sumi1[i,j,1] + 
        (PHI_I - PHI_B)*(1-r_IRS_Sumi1[i,j,1])*s_IRS_Sumi1[i,j,1] 
      ## probability of surviving biting given that there is ITN & IRS

      
      w_Acte1[i,j,2,2+cl[k]] = 1 - PHI_B + PHI_B*s_ITN[i+547]				 
      ## probability of surviving biting given that there is ITN
      w_Acte1[i,j,3,2+cl[k]] = 1 - PHI_I + PHI_I*(1-r_IRS_Acte1[i,j,2])*s_IRS_Acte1[i,j,2]	
      ##			probability of surviving biting given that there is IRS
      w_Acte1[i,j,4,2+cl[k]] = 1 - PHI_I + PHI_B*(1-r_IRS_Acte1[i,j,2])*s_ITN[i+547]*s_IRS_Acte1[i,j,2] + 
        (PHI_I - PHI_B)*(1-r_IRS_Acte1[i,j,2])*s_IRS_Acte1[i,j,2] 
      ## probability of surviving biting given that there is ITN & IRS
      
      w_Sumi1[i,j,2,2+cl[k]] = 1 - PHI_B + PHI_B*s_ITN[i+547]				 
      ## probability of surviving biting given that there is ITN
      w_Sumi1[i,j,3,2+cl[k]] = 1 - PHI_I + PHI_I*(1-r_IRS_Sumi1[i,j,2])*s_IRS_Sumi1[i,j,2]	
      ##			probability of surviving biting given that there is IRS
      w_Sumi1[i,j,4,2+cl[k]] = 1 - PHI_I + PHI_B*(1-r_IRS_Sumi1[i,j,2])*s_ITN[i+547]*s_IRS_Sumi1[i,j,2] + 
        (PHI_I - PHI_B)*(1-r_IRS_Sumi1[i,j,2])*s_IRS_Sumi1[i,j,2] 
      ## probability of surviving biting given that there is ITN & IRS

      
      w_Acte1[i,j,2,3+cl[k]] = 1 - PHI_B + PHI_B*s_ITN[i+547]				 
      ## probability of surviving biting given that there is ITN
      w_Acte1[i,j,3,3+cl[k]] = 1 - PHI_I + PHI_I*(1-r_IRS_Acte1[i,j,3])*s_IRS_Acte1[i,j,3]	
      ##			probability of surviving biting given that there is IRS
      w_Acte1[i,j,4,3+cl[k]] = 1 - PHI_I + PHI_B*(1-r_IRS_Acte1[i,j,3])*s_ITN[i+547]*s_IRS_Acte1[i,j,3] + 
        (PHI_I - PHI_B)*(1-r_IRS_Acte1[i,j,3])*s_IRS_Acte1[i,j,3] 
      ## probability of surviving biting given that there is ITN & IRS
      
      w_Sumi1[i,j,2,3+cl[k]] = 1 - PHI_B + PHI_B*s_ITN[i+547]				 
      ## probability of surviving biting given that there is ITN
      w_Sumi1[i,j,3,3+cl[k]] = 1 - PHI_I + PHI_I*(1-r_IRS_Sumi1[i,j,3])*s_IRS_Sumi1[i,j,3]	
      ##			probability of surviving biting given that there is IRS
      w_Sumi1[i,j,4,3+cl[k]] = 1 - PHI_I + PHI_B*(1-r_IRS_Sumi1[i,j,3])*s_ITN[i+547]*s_IRS_Sumi1[i,j,3] + 
        (PHI_I - PHI_B)*(1-r_IRS_Sumi1[i,j,3])*s_IRS_Sumi1[i,j,3] 
      ## probability of surviving biting given that there is ITN & IRS
      
    }
    
  }
  
}


prop_this_weekM = c(prop_houses_sprayed_WeeklyM[1],diff(prop_houses_sprayed_WeeklyM)[1:17])
prop_this_weekB = c(prop_houses_sprayed_WeeklyB[1],diff(prop_houses_sprayed_WeeklyB)[1:17])

w_Acte = yy_Acte = z_Acte = w_Sumi = yy_Sumi = z_Sumi = array(dim=c(365,4,9) )

for(j in 1:9){
  for(i in 1:365){
    w_Acte[i,1,j] = sum(w_Acte1[i,,1,j] * prop_this_weekM)
    w_Acte[i,2,j] = sum(w_Acte1[i,,2,j] * prop_this_weekM)
    w_Acte[i,3,j] = sum(w_Acte1[i,,3,j] * prop_this_weekM)
    w_Acte[i,4,j] = sum(w_Acte1[i,,4,j] * prop_this_weekM)
    
    w_Sumi[i,1,j] = sum(w_Sumi1[i,,1,j] * prop_this_weekB)
    w_Sumi[i,2,j] = sum(w_Sumi1[i,,2,j] * prop_this_weekB)
    w_Sumi[i,3,j] = sum(w_Sumi1[i,,3,j] * prop_this_weekB)
    w_Sumi[i,4,j] = sum(w_Sumi1[i,,4,j] * prop_this_weekB)
  }
  
}


## Probability of any bite (if there is IRS, a mosquito may bite and then die immediately afterwards)
yy_Acte[,1,] = w_Acte[,1,] 
yy_Acte[,2,] = w_Acte[,2,]

for(k in 1:3){
  for(j in 1:18){
    for(i in 1:365){
      PHI_B = PHI_B_mut[k]
      PHI_I = PHI_I_mut[k]
      
      yy_Acte1[i,j,3,1+cl[k]] = 1 - PHI_I + PHI_I*(1-r_IRS_Acte1[i,j,1])
      yy_Acte1[i,j,4,1+cl[k]] = 1 - PHI_I + PHI_B*(1-r_IRS_Acte1[i,j,1])*s_ITN[i+547] + 
        (PHI_I - PHI_B)*(1-r_IRS_Acte1[i,j,1])
      
      yy_Sumi1[i,j,3,1+cl[k]] = 1 - PHI_I + PHI_I*(1-r_IRS_Sumi1[i,j,1])
      yy_Sumi1[i,j,4,1+cl[k]] = 1 - PHI_I + PHI_B*(1-r_IRS_Sumi1[i,j,1])*s_ITN[i+547] + 
        (PHI_I - PHI_B)*(1-r_IRS_Sumi1[i,j,1])
      
      yy_Acte1[i,j,3,2+cl[k]] = 1 - PHI_I + PHI_I*(1-r_IRS_Acte1[i,j,2])
      yy_Acte1[i,j,4,2+cl[k]] = 1 - PHI_I + PHI_B*(1-r_IRS_Acte1[i,j,2])*s_ITN[i+547] + 
        (PHI_I - PHI_B)*(1-r_IRS_Acte1[i,j,2])
      
      yy_Sumi1[i,j,3,2+cl[k]] = 1 - PHI_I + PHI_I*(1-r_IRS_Sumi1[i,j,2])
      yy_Sumi1[i,j,4,2+cl[k]] = 1 - PHI_I + PHI_B*(1-r_IRS_Sumi1[i,j,2])*s_ITN[i+547] + 
        (PHI_I - PHI_B)*(1-r_IRS_Sumi1[i,j,2])
      
      yy_Acte1[i,j,3,3+cl[k]] = 1 - PHI_I + PHI_I*(1-r_IRS_Acte1[i,j,3])
      yy_Acte1[i,j,4,3+cl[k]] = 1 - PHI_I + PHI_B*(1-r_IRS_Acte1[i,j,3])*s_ITN[i+547] + 
        (PHI_I - PHI_B)*(1-r_IRS_Acte1[i,j,3])
      
      yy_Sumi1[i,j,3,3+cl[k]] = 1 - PHI_I + PHI_I*(1-r_IRS_Sumi1[i,j,3])
      yy_Sumi1[i,j,4,3+cl[k]] = 1 - PHI_I + PHI_B*(1-r_IRS_Sumi1[i,j,3])*s_ITN[i+547] + 
        (PHI_I - PHI_B)*(1-r_IRS_Sumi1[i,j,3])
      
    }
  }  
}

for(j in 1:9){
  for(i in 1:365){
    yy_Acte[i,3,j] = sum(yy_Acte1[i,,3,j] * prop_this_weekM)
    yy_Acte[i,4,j] = sum(yy_Acte1[i,,4,j] * prop_this_weekM)
    
    yy_Sumi[i,3,j] = sum(yy_Sumi1[i,,3,j] * prop_this_weekB)
    yy_Sumi[i,4,j] = sum(yy_Sumi1[i,,4,j] * prop_this_weekB)
  }  
}


## supplementary figure 1a
plot(yy_Acte[,1,1] ~ time[1:365],ylim=c(0,1),pch="",
     ylab = "Probability mosquito bites",
     col="black",
     main = "",cex.main=1.2,xlim=c(1,240),xaxt="n",
     xlab="Time in months",yaxt="n",cex.lab=1.4,cex.axis=1.4,cex=1.4)
axis(2,las=2,at=seq(0,1,0.2),labels=seq(0,1,0.2),cex.lab=1.4,cex.axis=1.4)
axis(1,at=seq(15,240,30),labels = c("Sep","Oct","Nov","Dec","Jan","Feb","Mar","Apr"),
     cex.axis = 1.4)

colsd=c("darkred","red","orange","blue")
for(i in 3){
  lines(yy_Acte[1:240,i,1] ~ time[1:240],col="darkblue",lwd=2)
  lines(yy_Sumi[1:240,i,1] ~ time[1:240],col="aquamarine3",lwd=2)
}

polygon(c(time[1:240],rev(time[1:240])),
        c(yy_Acte[1:240,3,5],rev(yy_Acte[1:240,3,9])),
        col=adegenet::transp("darkblue",0.3),border=NA)
polygon(c(time[1:240],rev(time[1:240])),
        c(yy_Sumi[1:240,3,5],rev(yy_Sumi[1:240,3,9])),
        col=adegenet::transp("aquamarine3",0.3),border=NA)


legend("bottomleft",legend = c("Actellic 300CS","SumiShield"),
       col = c("darkblue","aquamarine3"),lwd = 2, lty=c(1,1),cex=1.2,bty="n")

## 
plot(w_Acte[,1,1] ~ time[1:365],ylim=c(0,1),pch="",
     ylab = "Probability mosquito bites and survives",
     col="black",
     main = "",cex.main=1.2,xlim=c(1,240),xaxt="n",
     xlab="Time in months",yaxt="n",cex.lab=1.4,cex.axis=1.4,cex=1.4)
axis(2,las=2,at=seq(0,1,0.2),labels=seq(0,1,0.2),cex.lab=1.4,cex.axis=1.4)
axis(1,at=seq(15,240,30),labels = c("Sep","Oct","Nov","Dec","Jan","Feb","Mar","Apr"),
     cex.axis = 1.4)

colsd=c("darkred","red","orange","blue")
for(i in 3){
  lines(w_Acte[1:240,i,1] ~ time[1:240],col="darkblue",lwd = 2)
  lines(w_Sumi[1:240,i,1] ~ time[1:240],col="aquamarine3",lwd = 2)
}

polygon(c(time[1:240],rev(time[1:240])),
        c(w_Acte[1:240,3,5],rev(w_Acte[1:240,3,9])),
        col=adegenet::transp("darkblue",0.3),border=NA)
polygon(c(time[1:240],rev(time[1:240])),
        c(w_Sumi[1:240,3,5],rev(w_Sumi[1:240,3,9])),
        col=adegenet::transp("aquamarine3",0.3),border=NA)


## Probability repelled
z_Acte[,1,] = 0
z_Sumi[,1,] = 0

for(k in 1:3){
  for(j in 1:18){
    for(i in 1:365){
      PHI_B = PHI_B_mut[k]
      PHI_I = PHI_I_mut[k]
      z_Acte1[i,j,2,1+cl[k]] = PHI_B*r_ITN[i+547]
      z_Acte1[i,j,3,1+cl[k]] = PHI_I*r_IRS_Acte1[i,j,1]
      z_Acte1[i,j,4,1+cl[k]] = PHI_B*(r_IRS_Acte1[i,j,1] + (1-r_IRS_Acte1[i,j,1])*r_ITN[i+547]) + 
        (PHI_I - PHI_B)*r_IRS_Acte1[i,j,1]
      
      z_Sumi1[i,j,2,1+cl[k]] = PHI_B*r_ITN[i+547]
      z_Sumi1[i,j,3,1+cl[k]] = PHI_I*r_IRS_Sumi1[i,j,1]
      z_Sumi1[i,j,4,1+cl[k]] = PHI_B*(r_IRS_Sumi1[i,j,1] + (1-r_IRS_Sumi1[i,j,1])*r_ITN[i+547]) + 
        (PHI_I - PHI_B)*r_IRS_Sumi1[i,j,1]

      
      z_Acte1[i,j,2,2+cl[k]] = PHI_B*r_ITN[i+547]
      z_Acte1[i,j,3,2+cl[k]] = PHI_I*r_IRS_Acte1[i,j,2]
      z_Acte1[i,j,4,2+cl[k]] = PHI_B*(r_IRS_Acte1[i,j,2] + (1-r_IRS_Acte1[i,j,2])*r_ITN[i+547]) + 
        (PHI_I - PHI_B)*r_IRS_Acte1[i,j,2]
      
      z_Sumi1[i,j,2,2+cl[k]] = PHI_B*r_ITN[i+547]
      z_Sumi1[i,j,3,2+cl[k]] = PHI_I*r_IRS_Sumi1[i,j,2]
      z_Sumi1[i,j,4,2+cl[k]] = PHI_B*(r_IRS_Sumi1[i,j,2] + (1-r_IRS_Sumi1[i,j,2])*r_ITN[i+547]) + 
        (PHI_I - PHI_B)*r_IRS_Sumi1[i,j,2]

      z_Acte1[i,j,2,3+cl[k]] = PHI_B*r_ITN[i+547]
      z_Acte1[i,j,3,3+cl[k]] = PHI_I*r_IRS_Acte1[i,j,3]
      z_Acte1[i,j,4,3+cl[k]] = PHI_B*(r_IRS_Acte1[i,j,3] + (1-r_IRS_Acte1[i,j,3])*r_ITN[i+547]) + 
        (PHI_I - PHI_B)*r_IRS_Acte1[i,j,3]
      
      z_Sumi1[i,j,2,3+cl[k]] = PHI_B*r_ITN[i+547]
      z_Sumi1[i,j,3,3+cl[k]] = PHI_I*r_IRS_Sumi1[i,j,3]
      z_Sumi1[i,j,4,3+cl[k]] = PHI_B*(r_IRS_Sumi1[i,j,3] + (1-r_IRS_Sumi1[i,j,3])*r_ITN[i+547]) + 
        (PHI_I - PHI_B)*r_IRS_Sumi1[i,j,3]
      
    }  
  }
  
}

for(j in 1:9){
  for(i in 1:365){
    z_Acte[i,2,j] = sum(z_Acte1[i,,3,j] * prop_this_weekM)
    z_Acte[i,3,j] = sum(z_Acte1[i,,3,j] * prop_this_weekM)
    z_Acte[i,4,j] = sum(z_Acte1[i,,4,j] * prop_this_weekM)
    
    z_Sumi[i,2,j] = sum(z_Sumi1[i,,3,j] * prop_this_weekB)
    z_Sumi[i,3,j] = sum(z_Sumi1[i,,3,j] * prop_this_weekB)
    z_Sumi[i,4,j] = sum(z_Sumi1[i,,4,j] * prop_this_weekB)
  }
  
}


## supplementary figure 1c
plot(z_Acte[,1,1] ~ time[1:365],ylim=c(0,1),pch="",
     ylab = "Probability mosquito is repelled",
     col="black",
     main = "",cex.main=1.2,xlim=c(1,240),xaxt="n",
     xlab="Time in months",yaxt="n",cex.lab=1.4,cex.axis=1.4,cex=1.4)
axis(2,las=2,at=seq(0,1,0.2),labels=seq(0,1,0.2),cex.lab=1.4,cex.axis=1.4)
axis(1,at=seq(15,240,30),labels = c("Sep","Oct","Nov","Dec","Jan","Feb","Mar","Apr"),
     cex.axis = 1.4)

colsd=c("darkred","red","orange","blue")
for(i in 3){
  lines(z_Acte[1:240,i,1] ~ time[1:240],col="darkblue",lwd=2)
  lines(z_Sumi[1:240,i,1] ~ time[1:240],col="aquamarine3",lwd=2)
}


polygon(c(time[1:240],rev(time[1:240])),
        c(z_Acte[1:240,3,5],rev(z_Acte[1:240,3,9])),
        col=adegenet::transp("darkblue",0.3),border=NA)
polygon(c(time[1:240],rev(time[1:240])),
        c(z_Sumi[1:240,3,5],rev(z_Sumi[1:240,3,9])),
        col=adegenet::transp("aquamarine3",0.3),border=NA)


par(xpd=NA,cex = 1.11)

text(x = -650, y = 2.8,"(A)")
text(x = -340, y = 2.8,"(B)")
text(x = -38, y = 2.8,"(C)")

text(x = -650, y = 1.2,"(D)")
text(x = -340, y = 1.2,"(E)")
text(x = -38, y = 1.2,"(F)")

```


Having worked out the estimated probability of mosquito success in the presence of the sprays and under the conditions estimated for the two settings given the prolonged spray campaign, we adapt a mechanistic vector model approach determined in Le Menach 2007 (3) and Griffin et al (2010) (4) and updated in Walker et al 2016 (5).

In the next steps we estimate the relative lost protection, as a relative increase in probability of biting for people in the villages. We carry through the uncertainty from the section above. 


```{r echo = TRUE, eval = FALSE}

####################################
##
## Figure 5
##
####################################################


## waning usage of IRS with time


prop_mod_Acte_temp = c(0.891472868,0.81212081,0.639282555,0.481047262,0.386204738,0.304873387,0.166894353)

##And sorted for weeks:
prop_mod_Acte = c(rep(1,10),rep(prop_mod_Acte_temp,each=4))## for time series of spray campaign

true_cover_irs_Acte =  rep(prop_mod_Acte*0.96,each=7)

#House coverage: Matutuine district 96 %
irs_cov_no_loss_Acte = rep(0.96,30*8)
irs_cov_Acte = true_cover_irs_Acte


prop_mod_Sumi_temp = c(0.96460177,0.966330299,0.945153088,0.923357485,0.917585479,0.904508888,0.895619142)

##And sorted for weeks:
prop_mod_Sumi = c(rep(1,10),rep(prop_mod_Sumi_temp,each=4))## for time series of spray campaign

true_cover_irs_Sumi = rep(prop_mod_Sumi*prop_houses_sprayed_WeeklyB,each=7)

#House coverage: Boane (sumi) district 97 %, Manhica district (Palmeira) 98 % 
irs_cov_no_loss_Sumi = rep(0.97,30*8)
irs_cov_Sumi = rep(prop_mod_Sumi*0.97,each=7)

time = 1:365
plot(irs_cov_no_loss_Acte[61:240] ~ time[61:240],ylab = "Community IRS cover (%)",
     ylim=c(0,1),col="black",pch="",
     main = "",cex.main=1.2,xlim=c(1,240),xaxt="n",
     xlab="Time in months",yaxt="n",cex.lab=1.4,cex.axis=1.4,cex=1.4)
axis(2,las=2,at=seq(0,1,0.2),labels=seq(0,100,20),cex.lab=1.4,cex.axis=1.4)
axis(1,at=seq(0,230,30)+15,labels = c("Sep","Oct","Nov","Dec","Jan","Feb","Mar","Apr"),cex.axis = 1.4)


lines(irs_cov_no_loss_Acte[61:240] ~ time[61:240],lty=1,lwd=2,col = "darkblue") ## IRS only no loss 
lines(irs_cov_Acte[61:240] ~ time[61:240],lty=3,lwd=2,col = "darkblue") ## IRS with loss

lines(irs_cov_no_loss_Sumi[61:240] ~ c(time[61:240]+1),lty=1,lwd=2,col = "aquamarine3")
lines(irs_cov_Sumi[61:240] ~ time[61:240],lty=3,lwd=2,col = "aquamarine3")

legend("bottomleft",legend = c("Matutuine","Boane","IRS cover, no loss", "IRS cover, observed loss"),
       col = c("darkblue","aquamarine3","black","black"),lwd = 2, lty=c(NA,NA,1,3),
       pch=c(15,15,NA,NA),cex=1.2,bty="n")

cov1A = cov1S = cov2A = cov2S = array(dim=c(240,4))

# itn_cov_Acte = 0.52
# itn_cov_Sumi = 0.73

## Table 1 data
matu_net_cov = c(27.9,  ## nov
                 mean(c(32.6,42.1)), ##dec
                 mean(c(43.4,43.2,33.3)),##jan
                 mean(c(55.0,44.3,48.2)),##feb
                 mean(c(61.2,56.8,40.7)),##mar
                 mean(c(51.9,61.4,66.7)),##apr
                 mean(c(48.9,55.6)),##may
                 29.6)##june

itn_cov_Acte_temp = c(rep(mean(c(matu_net_cov)),10),
                      rep(mean(c(32.6,42.1)),4), ##dec
                      rep(mean(c(43.4,43.2,33.3)),4),##jan
                      rep(mean(c(55.0,44.3,48.2)),4),##feb
                      rep(mean(c(61.2,56.8,40.7)),4),##mar
                      rep(mean(c(51.9,61.4,66.7)),4),##apr
                      rep(mean(c(48.9,55.6)),4),##may
                      rep(29.6,4))##june



boan_net_cov = c(57.5,  ## nov
                 mean(c(64.6,74.5)), ##dec
                 mean(c(68.1,71.9,67.1)),##jan
                 mean(c(62.8,71.2,79)),##feb
                 mean(c(70.8,82.4,86.8)),##mar
                 mean(c(65.5,81.8,81.6)),##apr
                 mean(c(78.4,84.2)),##may
                 10.5)##june

itn_cov_Boan_temp = c(rep(mean(c(boan_net_cov)),10),
                      rep(mean(c(64.6,74.5)),4), ##dec
                      rep(mean(c(68.1,71.9,67.1)),4),##jan
                      rep(mean(c(62.8,71.2,79)),4),##feb
                      rep(mean(c(70.8,82.4,86.8)),4),##mar
                      rep(mean(c(65.5,81.8,81.6)),4),##apr
                      rep(mean(c(78.4,84.2)),4),##may
                      rep(10.5,4))

itn_cov_Acte = rep(itn_cov_Acte_temp,each=7)/100
itn_cov_Sumi = rep(itn_cov_Boan_temp,each=7)/100

## Here we are creating a matrix
## with the coverage or use of nets waning with time
## and the coverage of IRS either staying fixed, or also waning 
## when walls are washed
cov1A[,1] = 1
cov1A[,2] = itn_cov_Acte[1:240] ## ITN only
cov1A[,3] = irs_cov_no_loss_Acte ## IRS only
cov1A[,4] = itn_cov_Acte[1:240]*irs_cov_no_loss_Acte ## both interventions

cov2A[,1] = 1
cov2A[,2] = itn_cov_Acte[1:240] ## ITN only
cov2A[,3] = irs_cov_Acte[1:240] ## IRS only
cov2A[,4] = itn_cov_Acte[1:240]*irs_cov_Acte[1:240]## both interventions

cov1S[,1] = 1
cov1S[,2] = itn_cov_Sumi[1:240] ## ITN only
cov1S[,3] = irs_cov_no_loss_Sumi ## IRS only
cov1S[,4] = itn_cov_Sumi[1:240]*irs_cov_no_loss_Sumi ## both interventions

cov2S[,1] = 1
cov2S[,2] = itn_cov_Sumi[1:240] ## ITN only
cov2S[,3] = irs_cov_Sumi[1:240] ## IRS only
cov2S[,4] = itn_cov_Sumi[1:240]*irs_cov_Sumi[1:240] ## both interventions

## Entomological model parameters to estimate 

Q0 = 0.92  ## this is anthropophagy - we can use human blood index
chi = 0.86 ## this is endophily (pi_i)

fv0 = 0.333 ## biting rate 1 bite every 3 days
tau1 = 0.69 ## duration of host seeking, assumed to be constant between species (delta_10, altered to delta_1 when interventions used)
tau2 = 1/fv0-tau1  ## indoor feeding endophagy (delta_2)
av0 = Q0*fv0
mu0 = 0.132 ## background mortality from external sources
p10 = exp(-mu0*tau1) ## 
p2 = exp(-mu0*tau2)  ## probability of surviving resting period in absence of intervntion


## These are the adjusted w, z, when coverage is changing
## so these are the intervention coverages

## using the appropriate z_ and w_ arrays from above
## depending on whether we consider spray modifications over time or not
zhi1A = whi1A = zhi2A = whi2A = array(dim=c(240,4,9))
zhi1S = whi1S = zhi2S = whi2S = array(dim=c(240,4,9))
for(i in 1:9){
  zhi1A[,,i] = cov1A*z_Acte[1:240,,i]
  whi1A[,,i] = cov1A*w_Acte[1:240,,i]
  
  zhi1S[,,i] =cov1S*z_Sumi[1:240,,i]
  whi1S[,,i] =cov1S*w_Sumi[1:240,,i]
  
  
  zhi2A[,,i] =cov2A*z_Acte[1:240,,i]
  whi2A[,,i] =cov2A*w_Acte[1:240,,i]
  
  zhi2S[,,i] =cov2S*z_Sumi[1:240,,i]
  whi2S[,,i] =cov2S*w_Sumi[1:240,,i]
  
}


zbar1A = wbar1A = zbar2A = wbar2A = array(dim=c(240,4,9)) 
zbar1S = wbar1S = zbar2S = wbar2S = array(dim=c(240,4,9)) 
for(j in 1:9){
  for(i in 1:4){
    zbar1A[,i,j] = Q0*zhi1A[,i,j]
    wbar1A[,i,j] = (1 - Q0) + Q0*whi1A[,i,j]
    zbar2A[,i,j] = Q0*zhi2A[,i,j]
    wbar2A[,i,j] = (1 - Q0) + Q0*whi2A[,i,j]
    
    zbar1S[,i,j] = Q0*zhi1S[,i,j]
    wbar1S[,i,j] = (1 - Q0) + Q0*whi1S[,i,j]
    zbar2S[,i,j] = Q0*zhi2S[,i,j]
    wbar2S[,i,j] = (1 - Q0) + Q0*whi2S[,i,j]
  }
  
}
  

## From Walker et al 2016
## Mosquito feeding rate (tau1 is delta10, tau2 is delta2 in the methods)
fR1A = 1 / ((tau1/(1 - zbar1A)) + tau2)
mu1A = -fR1A*log((wbar1A*p10/(1 - zbar1A*p10))*p2) 
Q1A = 1 - (1-Q0)/wbar1A

fR2A = 1 / ((tau1/(1 - zbar2A)) + tau2)
mu2A = -fR2A*log((wbar2A*p10/(1 - zbar2A*p10))*p2) 
Q2A = 1 - (1-Q0)/wbar2A


fR1S = 1 / ((tau1/(1 - zbar1S)) + tau2)
mu1S = -fR1S*log((wbar1S*p10/(1 - zbar1S*p10))*p2) 
Q1S = 1 - (1-Q0)/wbar1S

fR2S = 1 / ((tau1/(1 - zbar2S)) + tau2)
mu2S = -fR2S*log((wbar2S*p10/(1 - zbar2S*p10))*p2) 
Q2S = 1 - (1-Q0)/wbar2S


## Rate at which a person in the popn is bitten by mosquitoes is
lambda1A = lambda2A = array(dim = c(240,4,9))
lambda1S = lambda2S = array(dim = c(240,4,9))

for(j in 1:9){
  for(i in 1:4){
    lambda1A[,,j] = (Q1A[,,j]*fR1A[,,j]*yy_Acte[,i,j])/whi1A[,i,j]
    lambda2A[,,j] = (Q2A[,,j]*fR2A[,,j]*yy_Acte[,i,j])/whi2A[,i,j]

    lambda1S[,,j] = (Q1S[,,j]*fR1S[,,j]*yy_Sumi[,i,j])/whi1S[,i,j]
    lambda2S[,,j] = (Q2S[,,j]*fR2S[,,j]*yy_Sumi[,i,j])/whi2S[,i,j]
    
  }
}




## Additional infectious bites per person per year 
Estimated_added_EIR = array(dim=c(240,2,9))
Estimated_added_EIR[,1,] = (lambda2A[,4,] - lambda1A[,4,])
Estimated_added_EIR[,2,] = (lambda2S[,4,] - lambda1S[,4,])

c(sum(Estimated_added_EIR[1:30,1,])/30,sum(Estimated_added_EIR[31:60,1,])/30,
  sum(Estimated_added_EIR[61:90,1,])/30,sum(Estimated_added_EIR[91:120,1,])/30,
  sum(Estimated_added_EIR[121:150,1,])/30,sum(Estimated_added_EIR[151:180,1,])/30)

c(sum(Estimated_added_EIR[1:30,2,])/30,sum(Estimated_added_EIR[31:60,2,])/30,
  sum(Estimated_added_EIR[61:90,2,])/30,sum(Estimated_added_EIR[91:120,2,])/30,
  sum(Estimated_added_EIR[121:150,2,])/30,sum(Estimated_added_EIR[151:180,2,])/30)


## Additional infectious bites per person per year 
Estimated_propn_increase_EIR = array(dim=c(240,2,9))
Estimated_propn_increase_EIR[,1,] = (lambda2A[,4,] - lambda1A[,4,])/lambda2A[,4,]
Estimated_propn_increase_EIR[,2,] = (lambda2S[,4,] - lambda1S[,4,])/lambda2S[,4,]

c(sum(Estimated_propn_increase_EIR[1:30,1,])/30,sum(Estimated_propn_increase_EIR[31:60,1,])/30,
  sum(Estimated_propn_increase_EIR[61:90,1,])/30,sum(Estimated_propn_increase_EIR[91:120,1,])/30,
  sum(Estimated_propn_increase_EIR[121:150,1,])/30,sum(Estimated_propn_increase_EIR[151:180,1,])/30)

c(sum(Estimated_propn_increase_EIR[1:30,2,])/30,sum(Estimated_propn_increase_EIR[31:60,2,])/30,
  sum(Estimated_propn_increase_EIR[61:90,2,])/30,sum(Estimated_propn_increase_EIR[91:120,2,])/30,
  sum(Estimated_propn_increase_EIR[121:150,2,])/30,sum(Estimated_propn_increase_EIR[151:180,2,])/30)

mean(Estimated_propn_increase_EIR[15:45,1,])##sep
mean(Estimated_propn_increase_EIR[46:75,1,])##oct
mean(Estimated_propn_increase_EIR[76:105,1,])##nov
mean(Estimated_propn_increase_EIR[106:135,1,])##dec
mean(Estimated_propn_increase_EIR[136:165,1,])##jan
mean(Estimated_propn_increase_EIR[166:195,1,])##feb
mean(Estimated_propn_increase_EIR[196:225,1,])##mar
mean(Estimated_propn_increase_EIR[226:240,1,])##part april

mean(Estimated_propn_increase_EIR[15:45,2,])##sep
mean(Estimated_propn_increase_EIR[46:75,2,])##oct
mean(Estimated_propn_increase_EIR[76:105,2,])##nov
mean(Estimated_propn_increase_EIR[106:135,2,])##dec
mean(Estimated_propn_increase_EIR[136:165,2,])##jan
mean(Estimated_propn_increase_EIR[166:195,2,])##feb
mean(Estimated_propn_increase_EIR[196:225,2,])##mar
mean(Estimated_propn_increase_EIR[226:240,2,])##part april

## Figure 5b

plot(Estimated_propn_increase_EIR[61:240,1,1] ~ time[61:240],ylim=c(0,1),pch="",
     ylab = "",
     col="black",
     main = "",cex.main=1.2,xlim=c(1,240),xaxt="n",
     xlab="Time in months",yaxt="n",cex.lab=1.4,cex.axis=1.4,cex=1.4)
mtext(side=2, line =4.3,
      "Relative increase in daily bites ")
mtext(side=2, line =3, "due to modifications (%)")
axis(2,las=2,at=seq(0,1,0.2),label=seq(0,100,20),cex.lab=1.4,cex.axis=1.4)

axis(1,at=seq(0,230,30)+15,labels = c("Sep","Oct","Nov","Dec","Jan","Feb","Mar","Apr"),cex.axis = 1.4)

colsd = c("darkblue","aquamarine3")
for(i in 1:2){
  lines(Estimated_propn_increase_EIR[61:240,i,1] ~ time[61:240],col=colsd[i],lty=2,lwd=2)
}

min_EIR = max_EIR = array(dim=c(length(61:240),2))
for(j in 1:2){
  for(i in 1:length(61:240)){
    min_EIR[i,j] = min(Estimated_propn_increase_EIR[60+i,j,])
    max_EIR[i,j] = max(Estimated_propn_increase_EIR[60+i,j,])
    
  }  
}

polygon(c(time[61:240],rev(time[61:240])),
        c(min_EIR[,1],rev(max_EIR[,1])),
        col=adegenet::transp("darkblue",0.3),border=NA)
polygon(c(time[61:240],rev(time[61:240])),
        c(min_EIR[,2],rev(max_EIR[,2])),
        col=adegenet::transp("aquamarine",0.3),border=NA)



Estimated_added_EIR = array(dim=c(240,2,9))
Estimated_added_EIR[,1,] = (lambda2A[,3,] - lambda1A[,3,])
Estimated_added_EIR[,2,] = (lambda2S[,3,] - lambda1S[,3,])

## Additional infectious bites per person per year 
Estimated_propn_increase_EIR = array(dim=c(240,2,9))
Estimated_propn_increase_EIR[,1,] = (lambda2A[,3,] - lambda1A[,3,])/lambda2A[,3,]
Estimated_propn_increase_EIR[,2,] = (lambda2S[,3,] - lambda1S[,3,])/lambda2S[,3,]

for(i in 1:2){
  lines(Estimated_propn_increase_EIR[61:240,i,1] ~ time[61:240],col=colsd[i],lty=1,lwd=1)
}

min_EIR = max_EIR = array(dim=c(length(61:240),2))
for(j in 1:2){
  for(i in 1:length(61:240)){
    min_EIR[i,j] = min(Estimated_propn_increase_EIR[60+i,j,])
    max_EIR[i,j] = max(Estimated_propn_increase_EIR[60+i,j,])
    
  }  
}

polygon(c(time[61:240],rev(time[61:240])),
        c(min_EIR[,1],rev(max_EIR[,1])),
        col=adegenet::transp("darkblue",0.3),border=NA)
polygon(c(time[61:240],rev(time[61:240])),
        c(min_EIR[,2],rev(max_EIR[,2])),
        col=adegenet::transp("aquamarine",0.3),border=NA)


mean(Estimated_propn_increase_EIR[1:30,1,])
mean(Estimated_propn_increase_EIR[31:60,1,])
mean(Estimated_propn_increase_EIR[61:92,1,])
mean(Estimated_propn_increase_EIR[93:122,1,])
mean(Estimated_propn_increase_EIR[123:153,1,])
mean(Estimated_propn_increase_EIR[154:180,1,])


legend("topleft",legend = c("Matutuine (assuming no LLIN)","Boane (assuming no LLIN)",
                            "Matutuine (LLIN use)","Boane (LLIN use)"),
       col = c("darkblue","aquamarine3","darkblue","aquamarine3"),lwd = c(2,2,1,1), lty=c(1,1,2,2),cex=1.2,bty="n")



#############################
## 
## this is repeated for the spray modification over time

##Species are different in each location 
PHI_B_mut = c(0.85,0.6,0.95) ## probability of bites in bed
PHI_I_mut = c(0.90,0.68,0.99) ## probability of bites indoors

PHI_B_boa = c(0.85,0.6,0.95)  ## probability of bites in bed
PHI_I_boa = c(0.90,0.68,0.99) ## probability of bites indoors

## Data for the proportion of houses sprayed
## over the course of the trial
prop_houses_sprayed_WeeklyB = 0.97*c(0,	0.027219794,	## August
                                0.077014558,	0.136261919,	0.196901742,	0.250817066, ## Sept
                                0.301047746,	0.347687015,	0.395348206,	0.464541108, ## Oct
                                0.521818166,	0.581372602,	0.643327061,	0.710948828, ## Nov
                                0.777620537,	0.847130239,	0.911498024,	0.930365931, ## Dec
                                0.947042313,	0.96389906,	0.983400068,	0.991357264,	 ## Jan
                                0.99238783,	1) ## Feb
prop_houses_sprayed_WeeklyM = 0.96*c(0.065358837,	0.193716785,## August
                                0.334444596,	0.432141444,	0.533708885,	0.614060416,##sep
                                0.667531537,	0.711462198,	0.769981823,	0.880751007,##oct
                                0.919045204,	0.944027976,	0.97443187,	0.990922736,  ##nov
                                0.991873307,	0.99744169,	 1,             1,          ##dec
                                1,        1) ## jan


## from Table 1 main manuscript 

## Accounting for modifications and added rooms in OCT cohort we have
cov_a_oct = c(0.891472868,0.776978417,0.556962025, 0.393063584,0.302702703, 0.218274112)
## Accounting for modifications and added rooms in NOV cohort we have
cov_a_nov = c(0.863636364,0.694736842,0.538461538,0.426086957,0.341269841,0.288888889)
## Accounting for modifications and added rooms in DEC cohort we have
cov_a_dec = c(0.851851852,0.714285714,0.655172414,0.6,0.566666667,0.548387097)

## Accounting for modifications and added rooms in OCT cohort we have
cov_s_oct = c(0.96460177,0.956140351,0.930434783,0.922413793,0.922413793,0.914529915)
## Accounting for modifications and added rooms in NOV cohort we have
cov_s_nov = c(0.973856209,0.948387097,0.918238994,0.918238994,0.900621118,0.895061728)
## Accounting for modifications and added rooms in DEC cohort we have
cov_s_dec = c(0.960526316,0.935064935,0.909090909,0.897435897,0.897435897,0.897435897)

## And weighting for the proportion of people represented in each survey 129:88:27 for Mut and 113:153:76 for Boane

prop_mod_Acte_temp = c(0.891472868,0.81212081,0.639282555,0.481047262,0.386204738,0.304873387,0.166894353)

##And sorted for weeks:
prop_mod_Acte = c(rep(1,10),rep(prop_mod_Acte_temp,each=4))## for time series of spray campaign

true_cover_irs_Acte =  rep(prop_mod_Acte*prop_houses_sprayed_WeeklyM,each=7)

#House coverage: Matutuine district 96 %
irs_cov_no_loss_Acte = rep(0.96,30*8)
irs_cov_Acte = true_cover_irs_Acte


prop_mod_Sumi_temp = c(0.96460177,0.966330299,0.945153088,0.923357485,0.917585479,0.904508888,0.895619142)

##And sorted for weeks:
prop_mod_Sumi = c(rep(1,10),rep(prop_mod_Sumi_temp,each=4))## for time series of spray campaign

true_cover_irs_Sumi = rep(prop_mod_Sumi*prop_houses_sprayed_WeeklyB,each=7)

#House coverage: Boane (sumi) district 97 %, Manhica district (Palmeira) 98 % 
irs_cov_no_loss_Sumi = rep(0.97,30*8)
irs_cov_Sumi = true_cover_irs_Sumi

plot(irs_cov_no_loss_Acte[1:240] ~ time[1:240],ylab = "Community IRS cover (%)",
     ylim=c(0,1),col="black",pch="",
     main = "",cex.main=1.2,xlim=c(1,240),xaxt="n",
     xlab="Time in months",yaxt="n",cex.lab=1.4,cex.axis=1.4,cex=1.4)
axis(2,las=2,at=seq(0,1,0.2),labels=seq(0,100,20),cex.lab=1.4,cex.axis=1.4)
axis(1,at=seq(0,230,30)+15,labels = c("Sep","Oct","Nov","Dec","Jan","Feb","Mar","Apr"),cex.axis = 1.4)


lines(irs_cov_no_loss_Acte[61:240] ~ time[61:240],lty=1,lwd=2,col = "darkblue")
lines(irs_cov_Acte[61:240] ~ time[61:240],lty=3,lwd=2,col = "darkblue")

lines(irs_cov_no_loss_Sumi[61:240] ~ c(time[61:240]+1),lty=1,lwd=2,col = "aquamarine3")
lines(irs_cov_Sumi[61:240] ~ time[61:240],lty=3,lwd=2,col = "aquamarine3")

cov1A = cov1S = cov2A = cov2S = array(dim=c(240,4))

# itn_cov_Acte = 0.52
# itn_cov_Sumi = 0.73

## Table 1 data
matu_net_cov = c(27.9,  ## nov
                 mean(c(32.6,42.1)), ##dec
                 mean(c(43.4,43.2,33.3)),##jan
                 mean(c(55.0,44.3,48.2)),##feb
                 mean(c(61.2,56.8,40.7)),##mar
                 mean(c(51.9,61.4,66.7)),##apr
                 mean(c(48.9,55.6)),##may
                 29.6)##june

itn_cov_Acte_temp = c(rep(mean(c(matu_net_cov)),10),
                   rep(mean(c(32.6,42.1)),4), ##dec
                   rep(mean(c(43.4,43.2,33.3)),4),##jan
                   rep(mean(c(55.0,44.3,48.2)),4),##feb
                   rep(mean(c(61.2,56.8,40.7)),4),##mar
                   rep(mean(c(51.9,61.4,66.7)),4),##apr
                   rep(mean(c(48.9,55.6)),4),##may
                   rep(29.6,4))##june



boan_net_cov = c(57.5,  ## nov
                 mean(c(64.6,74.5)), ##dec
                 mean(c(68.1,71.9,67.1)),##jan
                 mean(c(62.8,71.2,79)),##feb
                 mean(c(70.8,82.4,86.8)),##mar
                 mean(c(65.5,81.8,81.6)),##apr
                 mean(c(78.4,84.2)),##may
                 10.5)##june

itn_cov_Boan_temp = c(rep(mean(c(boan_net_cov)),10),
                      rep(mean(c(64.6,74.5)),4), ##dec
                      rep(mean(c(68.1,71.9,67.1)),4),##jan
                      rep(mean(c(62.8,71.2,79)),4),##feb
                      rep(mean(c(70.8,82.4,86.8)),4),##mar
                      rep(mean(c(65.5,81.8,81.6)),4),##apr
                      rep(mean(c(78.4,84.2)),4),##may
                      rep(10.5,4))

itn_cov_Acte = rep(itn_cov_Acte_temp,each=7)/100
itn_cov_Sumi = rep(itn_cov_Boan_temp,each=7)/100

## Here we are creating a matrix
## with the coverage or use of nets waning with time
## and the coverage of IRS either staying fixed, or also waning 
## when walls are washed
cov1A[,1] = 1
cov1A[,2] = itn_cov_Acte[1:240] ## ITN only
cov1A[,3] = irs_cov_no_loss_Acte ## IRS only
cov1A[,4] = itn_cov_Acte[1:240]*irs_cov_no_loss_Acte ## both interventions

cov2A[,1] = 1
cov2A[,2] = itn_cov_Acte[1:240] ## ITN only
cov2A[,3] = irs_cov_Acte[1:240] ## IRS only
cov2A[,4] = itn_cov_Acte[1:240]*irs_cov_Acte[1:240]## both interventions

cov1S[,1] = 1
cov1S[,2] = itn_cov_Sumi[1:240] ## ITN only
cov1S[,3] = irs_cov_no_loss_Sumi ## IRS only
cov1S[,4] = itn_cov_Sumi[1:240]*irs_cov_no_loss_Sumi ## both interventions

cov2S[,1] = 1
cov2S[,2] = itn_cov_Sumi[1:240] ## ITN only
cov2S[,3] = irs_cov_Sumi[1:240] ## IRS only
cov2S[,4] = itn_cov_Sumi[1:240]*irs_cov_Sumi[1:240] ## both interventions

## These are the adjusted w, z, when coverage is changing
## so these are the intervention coverages
zhi1A = whi1A = zhi2A = whi2A = array(dim=c(240,4,9))
zhi1S = whi1S = zhi2S = whi2S = array(dim=c(240,4,9))
for(i in 1:9){
  zhi1A[,,i]=cov1A*z_Acte[1:240,,i]
  whi1A[,,i]=cov1A*w_Acte[1:240,,i]
  
  zhi1S[,,i]=cov1S*z_Sumi[1:240,,i]
  whi1S[,,i]=cov1S*w_Sumi[1:240,,i]
  
  
  zhi2A[,,i]=cov2A*z_Acte[1:240,,i]
  whi2A[,,i]=cov2A*w_Acte[1:240,,i]
  
  zhi2S[,,i]=cov2S*z_Sumi[1:240,,i]
  whi2S[,,i]=cov2S*w_Sumi[1:240,,i]
  
}



zbar1A = wbar1A = zbar2A = wbar2A = array(dim=c(240,4,9)) 
zbar1S = wbar1S = zbar2S = wbar2S = array(dim=c(240,4,9))
for(j in 1:9){
  for(i in 1:4){
    zbar1A[,i,j] = Q0*zhi1A[,i,j]
    wbar1A[,i,j] = (1 - Q0) + Q0*whi1A[,i,j]
    zbar2A[,i,j] = Q0*zhi2A[,i,j]
    wbar2A[,i,j] = (1 - Q0) + Q0*whi2A[,i,j]
    
    zbar1S[,i,j] = Q0*zhi1S[,i,j]
    wbar1S[,i,j] = (1 - Q0) + Q0*whi1S[,i,j]
    zbar2S[,i,j] = Q0*zhi2S[,i,j]
    wbar2S[,i,j] = (1 - Q0) + Q0*whi2S[,i,j]
  }  
}


## From Walker et al 2016
## Mosquito feeding rate (tau1 is delta10, tau2 is delta2 in the methods)
fR1A = 1 / ((tau1/(1 - zbar1A)) + tau2)
mu1A = -fR1A*log((wbar1A*p10/(1 - zbar1A*p10))*p2) 
Q1A = 1 - (1-Q0)/wbar1A

fR2A = 1 / ((tau1/(1 - zbar2A)) + tau2)
mu2A = -fR2A*log((wbar2A*p10/(1 - zbar2A*p10))*p2) 
Q2A = 1 - (1-Q0)/wbar2A


fR1S = 1 / ((tau1/(1 - zbar1S)) + tau2)
mu1S = -fR1S*log((wbar1S*p10/(1 - zbar1S*p10))*p2) 
Q1S = 1 - (1-Q0)/wbar1S

fR2S = 1 / ((tau1/(1 - zbar2S)) + tau2)
mu2S = -fR2S*log((wbar2S*p10/(1 - zbar2S*p10))*p2) 
Q2S = 1 - (1-Q0)/wbar2S

## Rate at which a person in the popn is bitten by mosquitoes is
lambda1A = lambda2A = array(dim = c(240,4,9))
lambda1S = lambda2S = array(dim = c(240,4,9))
for(j in 1:9){
  for(i in 1:4){
    lambda1A[,,j] = (Q1A[,,j]*fR1A[,,j]*yy_Acte[1:240,i,j])/whi1A[1:240,i,j]
    lambda2A[,,j] = (Q2A[,,j]*fR2A[,,j]*yy_Acte[1:240,i,j])/whi2A[1:240,i,j]
    
    lambda1S[,,j] = (Q1S[,,j]*fR1S[,,j]*yy_Sumi[1:240,i,j])/whi1S[1:240,i,j]
    lambda2S[,,j] = (Q2S[,,j]*fR2S[,,j]*yy_Sumi[1:240,i,j])/whi2S[1:240,i,j]
  }  
}


## Additional infectious bites per person per year 
Estimated_propn_increase_EIR = array(dim=c(240,2,9))
Estimated_propn_increase_EIR[,1,] = (lambda2A[,4,] - lambda1A[,4,])/lambda2A[,4,]
Estimated_propn_increase_EIR[,2,] = (lambda2S[,4,] - lambda1S[,4,])/lambda2S[,4,]

c(sum(Estimated_propn_increase_EIR[1:30,1,])/30,sum(Estimated_propn_increase_EIR[31:60,1,])/30,
  sum(Estimated_propn_increase_EIR[61:90,1,])/30,sum(Estimated_propn_increase_EIR[91:120,1,])/30,
  sum(Estimated_propn_increase_EIR[121:150,1,])/30,sum(Estimated_propn_increase_EIR[151:180,1,])/30)

c(sum(Estimated_propn_increase_EIR[1:30,2,])/30,sum(Estimated_propn_increase_EIR[31:60,2,])/30,
  sum(Estimated_propn_increase_EIR[61:90,2,])/30,sum(Estimated_propn_increase_EIR[91:120,2,])/30,
  sum(Estimated_propn_increase_EIR[121:150,2,])/30,sum(Estimated_propn_increase_EIR[151:180,2,])/30)

mean(Estimated_propn_increase_EIR[15:45,1,])##sep
mean(Estimated_propn_increase_EIR[46:75,1,])##oct
mean(Estimated_propn_increase_EIR[76:105,1,])##nov
mean(Estimated_propn_increase_EIR[106:135,1,])##dec
mean(Estimated_propn_increase_EIR[136:165,1,])##jan
mean(Estimated_propn_increase_EIR[166:195,1,])##feb
mean(Estimated_propn_increase_EIR[196:225,1,])##mar
mean(Estimated_propn_increase_EIR[226:240,1,])##part april

mean(Estimated_propn_increase_EIR[15:45,2,])##sep
mean(Estimated_propn_increase_EIR[46:75,2,])##oct
mean(Estimated_propn_increase_EIR[76:105,2,])##nov
mean(Estimated_propn_increase_EIR[106:135,2,])##dec
mean(Estimated_propn_increase_EIR[136:165,2,])##jan
mean(Estimated_propn_increase_EIR[166:195,2,])##feb
mean(Estimated_propn_increase_EIR[196:225,2,])##mar
mean(Estimated_propn_increase_EIR[226:240,2,])##part april


plot(Estimated_propn_increase_EIR[,1,1] ~ time[1:240],ylim=c(0,1),pch="",
     ylab = "",
     col="black",
     main = "",cex.main=1.2,xlim=c(1,240),xaxt="n",
     xlab="Time in months",yaxt="n",cex.lab=1.4,cex.axis=1.4,cex=1.4)
axis(2,las=2,at=seq(0,1,0.2),labels=seq(0,100,20),cex.lab=1.4,cex.axis=1.4)
axis(1,at=seq(0,230,30)+15,labels = c("Sep","Oct","Nov","Dec","Jan","Feb","Mar","Apr"),cex.axis = 1.4)
mtext(side=2, line =4.3,
      "Relative increase in daily bites")
mtext(side=2, line =3, "due to spray campaign & modifications (%)")

colsd = c("darkblue","aquamarine3")
for(i in 1:2){
  lines(Estimated_propn_increase_EIR[61:240,i,1] ~ time[61:240],col=colsd[i],lty=2,lwd=2)
}

min_EIR = max_EIR = array(dim=c(length(61:240),2))
for(j in 1:2){
  for(i in 1:length(61:240)){
    min_EIR[i,j] = min(Estimated_propn_increase_EIR[60+i,j,])
    max_EIR[i,j] = max(Estimated_propn_increase_EIR[60+i,j,])
    
  }  
}

polygon(c(time[61:240],rev(time[61:240])),
        c(min_EIR[,1],rev(max_EIR[,1])),
        col=adegenet::transp("darkblue",0.3),border=NA)
polygon(c(time[61:240],rev(time[61:240])),
        c(min_EIR[,2],rev(max_EIR[,2])),
        col=adegenet::transp("aquamarine",0.3),border=NA)



Estimated_added_EIR = array(dim=c(240,2,9))
Estimated_added_EIR[,1,] = (lambda2A[,3,] - lambda1A[,3,])
Estimated_added_EIR[,2,] = (lambda2S[,3,] - lambda1S[,3,])

## Additional infectious bites per person per year 
Estimated_propn_increase_EIR = array(dim=c(240,2,9))
Estimated_propn_increase_EIR[,1,] = (lambda2A[,3,] - lambda1A[,3,])/lambda2A[,3,]
Estimated_propn_increase_EIR[,2,] = (lambda2S[,3,] - lambda1S[,3,])/lambda2S[,3,]

for(i in 1:2){
  lines(Estimated_propn_increase_EIR[61:240,i,1] ~ time[61:240],col=colsd[i],lty=1,lwd=1)
}

min_EIR = max_EIR = array(dim=c(length(61:240),2))
for(j in 1:2){
  for(i in 1:length(61:240)){
    min_EIR[i,j] = min(Estimated_propn_increase_EIR[60+i,j,])
    max_EIR[i,j] = max(Estimated_propn_increase_EIR[60+i,j,])
    
  }  
}

polygon(c(time[61:240],rev(time[61:240])),
        c(min_EIR[,1],rev(max_EIR[,1])),
        col=adegenet::transp("darkblue",0.3),border=NA)
polygon(c(time[61:240],rev(time[61:240])),
        c(min_EIR[,2],rev(max_EIR[,2])),
        col=adegenet::transp("aquamarine",0.3),border=NA)


par(xpd=NA,cex = 1.11)



```


## References

1. Sherrard-Smith E, Winskill P, Corbel V, Pennetier C, Djénontin A, Moore S, Richardson JH, Müller P, Edi C, Protopopoff N, Oxborough R, Agossa F, N'Guessan R, Rowland M, Churcher TS. 2018. Systematic review of indoor residual spray efficacy and effectiveness against Plasmodium falciparum in Africa. Nat Communs.9. 4982. DOI: 10.1038/s41467-018-07357-w

2. Churcher TS, Lissenden N, Griffin JT, Worrall E, Ranson H. 2016.The impact of pyrethroid resistance on the efficacy and effectiveness of bednets for malaria control in Africa. ELife 5. DOI: 10.7554/eLife.16090

3. Le Menach A, Takala S, McKenzie FE, Perisse A, Harris A, Flahault A, Smith DL. 2007. An elaborated feeding cycle model for reductions in vectorial capacity of night-biting mosquitoes by insecticide-treated nets. Malar J. 6. 10

4. Griffin JT, Hollingsworth D, Okell LC, Churcher TS, White M, Hinsley W, Bousema T, Drakeley CJ, Ferguson NM, Basáñez M-G, Ghani AC. 2010. Reducing Plasmodium falciparum malaria transmission in Africa: a model-based evaluation of intervention strategies. PLoS Med. 7. e1000324. DOI:10.1371/journal.pmed.1000324

5. Walker PGT, Griffin JT, Ferguson NM, Ghani AC. 2016. Estimating the most efficient allocation of interventions to achieve reductions in Plasmodium falciparum malaria burden and transmission in Africa: a modelling study. Lancet Global Health. 4. e474-84. DOI: 10.1016/S2214-109X(16)30073-0  

6. Sherrard-Smith E, ... 2019. PNAS
